### 2012-05-03 paper/paper.tex
Texified design and methodology

\documentclass[12pt]{article}

\usepackage{fullpage}

\title{Sr: Processing Data Streams By Doing Less Work}
\author{Ryan Lopopolo\\
\texttt{lopopolo@mit.edu}}

\begin{document}
\twocolumn
\maketitle

\section{Design}
Sr is a distributed system for processing streams that can choose to kill tasks or limit the amount of work it performs per task. Its design is modular; there are five different types of nodes in an Sr cluster (spout, fetcher, worker, collector, master).
\subsection{Spout}
Spouts are network-connected machines that generate data for the Sr cluster to process. Examples include a machine that tails a log file or an API like the Twitter tweet stream. Fetchers depend on spouts as a source of streaming data.
\subsection{Fetcher}
Fetchers are responsible for communicating with spouts and returning data for the workers to process. Fetchers may run indefinitely or return a status code indicating the fetching task is over.
\subsection{Worker}
Workers perform processing on data provided by fetchers. They are similar to mappers in the MapReduce framework. Each worker receives a fraction of the total input data and each worker’s tasks are independent of other workers’.

Workers are responsible for fulfilling the main design goals of Sr. Workers may choose to kill a task preemptively or if it does not complete before a timeout. Additionally, workers may choose among a variety of routines for performing computation on a datum. Routines are ranked on a [0,1] scale based on the estimated fraction of total work it requires.

As it runs, a worker maintains an internal metric that estimates the fraction of work it has performed over all data it has seen. Workers use this metric when choosing which computation routine to run for a datum. A worker will choose the lowest ranked routine such that its estimated fraction of work is above a configured threshold.

Because one of Sr’s goals is to process (potentially infinite) streams, workers do not save their progress to disk and are forgetful; once the master queries a worker for its progress and the worker successfully returns it, the worker clears all of its state and continues processing. As a consequence, workers are easy to add or remove from the worker pool because they don’t need to be initialized with long-term job state. Additionally, as long as the master polls workers frequently enough, when a worker fails, only a small fraction of the total work is lost. The master queries workers every 100ms by default.
\subsection{Collector}
Collector nodes aggregate the results of all workers. Each collector acts as a reducer in the MapReduce framework if MapReduce used a single reducer for all of the mappers. Collectors differ from MapReduce reducers in that they receive their data piecewise, as it is produced from workers as opposed to after all mappers have completed. This limits the type of aggregation collectors can do to online operations.

Collectors also expose an API endpoint for accessing the results of a job. This endpoint can be used by another spout to chain Sr jobs together.
\subsection{Master}
There is one master node per Sr network. It has a function similar to the jobtracker in MapReduce. New jobs are scheduled with the master and it initializes other nodes in the cluster with job state. For each job, the master schedules roles among nodes in a round robin manner to minimize the total number of outstanding roles on any one node.

The master is the only well-known node in the cluster. Other nodes in the network exclusively communicate with the master. The master and other nodes communicate with each other by issuing HTTP requests to a simple server on each node. I decided to make use of a library [Sinatra.rb] providing the server functionality because there was a low barrier to getting inter-node communication functioning. This design choice presents some problems and will be discussed further in section 5.

Another consequence of the master being the only well-known node is that all data in the cluster must flow through it. The master maintains two queues per job for buffering job progress from fetchers and workers and periodically pushes this state out to workers and collectors, respectively.
\subsection{Configuring a Cluster for a Job}
Apart from spouts, all nodes in a cluster modify their behavior based on the job they are running. The master must know the appropriate number of nodes to spin up; fetchers need to know how to talk to spouts; workers need to know how to compute results; and collectors need to know how to combine batched worker results.

Sr accomplishes this configuration with a Jobfile. Jobfiles are instances of a special class provided by the Sr framework. This class exposes several methods that can be invoked by a given node to provide configuration parameters or execute code on its behalf. Most of the routines that advance the progress of an Sr job are wrappers around these Jobfile methods.

Sr sends the source of the Jobfile to every node participating in the job and uses eval to obtain a local instance of the Jobfile class. An example jobfile can be found at [github].

The use of eval to instantiate Jobfile objects and the implementation language’s (Ruby) ability to monkeypatch classes means that jobs can be modified on the fly just by sending an updated Jobfile to job participants. For example, a job can be made lower fidelity in the face of an impending time constraint or higher fidelity if more workers are added to the cluster.
\subsection{Fault Tolerance}
Sr can sustain the failure of any node other than the master. Because the master is responsible for shuffling data between fetchers, workers, and collectors, a job cannot make progress without the master.

Fetchers can fail. The only consequence of fetcher failure is that some of the input stream is lost forever. Since streams contain much data and are likely stored permanently elsewhere on disk, Sr does not attempt to recover this data.

Worker failures may entail some lost work. Having the master poll each worker frequently for its progress mitigates the consequences of worker failure. For jobs that run for minutes or hours, 100ms of lost work is << 0.1% of the total. Sr can simply treat these lost tasks as preemptively killed, which is already expected by the cluster.

Each collector is an exact replica of all others. Collector failure does not impact correctness of the results delivered by any other collector.
\subsection{Killing Tasks and Working Less}
A design goal of Sr is to compute meaningful results from a stream and to do so while not processing every datum one-to-one. Sr achieves this goal in two different ways. First, workers may kill tasks preemptively to avoid the time and resource costs associated with processing that task. Second, workers rely on the Jobfile to provide them with several different computation routines of differing fidelities that perform a fraction of the total work on a datum.

These behaviors appeal to the law of large numbers. It assumes that trends will still be visible in spite of looking at only a fraction of the data. This means that the computation routines and the weights assigned to them must be adapted to fit the distribution of the data before the job starts (or updated in situ via a new Jobfile).

\section{Methodology}
The cluster I used to test Sr is a 5-node network consisting of 1 spout, 1 fetcher, 4 workers, 1 collector, and 1 master. Roles are partitioned among nodes as shown in figure 1. Worker nodes were XVM [SIPB] VMs provisioned with 128MB RAM each. The master, spout, fetcher, and collector ran on my laptop, a mid-2010 Macbook Air with 4GB of RAM.

\begin{figure}
\begin{verbatim}
                  |--------|
                - | worker | 
               /  |--------|
|-----------| /   |--------|
| master    | --- | worker |
| spout     |     |--------|
| fetcher   |     |--------|
| collector | --- | worker |
|-----------| \   |--------|
               \  |--------|
                - | worker |
                  |--------|

\end{verbatim}
\caption{Topology of the test Sr cluster. Each box is a single machine.}
\end{figure}

The job I ran was a word counter. The collector emits a hash whose keys are words and whose values are the frequency that word has occurred in the test corpus.

To run the job, I had to create a spout and find a source of data. For data, I acquired a Wikipedia dump of the Featured Articles category. I used Wikipedia’s xml exporter [Special:export] on January 9, 2012.

To serve the data, I munged it into a YAML file containing a hash of \texttt{article\_id => fulltext}. To store fulltext, I base64 encoded it and deflated it. This requires workers to inflate and decode the fulltext before they can process it further. The server reads from this YAML file and returns the resulting hash as JSON.

The fetcher communicates to the spout by requesting sequential article ids until it has fetched every article.

Workers are initialized with the 3 computation routines shown in table 1.

\begin{center}
\begin{table}
\begin{tabular}{|l|p{5cm}|}
 \hline
Weight & Description \\ \hline
1.0 & Deflate and decode fulltext and count words in all of fulltext \\ \hline
0.25 & Deflate and decode fulltext and count words in approximately a quarter of fulltext \\ \hline
0.1 & Return the results of the last computation from a cache \\ \hline
\end{tabular}
\caption{Computation routines used by Sr workers}
\end{table}
\end{center}

\end{document}

### 2012-05-03 paper/paper.tex
Remove extra space from the verbatim block
add all section headers
Add start of evaluation section and referencify table and figures

@@
 \usepackage{fullpage}
+\usepackage{listings}
+\usepackage{graphicx}
+\graphicspath{{images/}}
 
@@
 \maketitle
+
+\section{Introduction}
+
+\section{Related Work}
 
@@
 The cluster I used to test Sr is a 5-node network consisting of 1 spout, 1 fetcher, 4 workers, 1 collector, and 1 master.
-Roles are partitioned among nodes as shown in figure 1.
+Roles are partitioned among nodes as shown in Figure ~\ref{fig:clusterDiagram}.
 Worker nodes were XVM [SIPB] VMs provisioned with 128MB RAM each.
@@
 \caption{Topology of the test Sr cluster. Each box is a single machine.}
+\label{fig:clusterDiagram}
 \end{figure}
@@
 
-To serve the data, I munged it into a YAML file containing a hash of \texttt{article\_id => fulltext}.
+To serve the data, I munged it into a YAML file containing a hash of \lstinline[language=Ruby]{article_id : fulltext}.
 To store fulltext, I base64 encoded it and deflated it.
@@
 
-Workers are initialized with the 3 computation routines shown in table 1.
+Workers are initialized with the 3 computation routines shown in Table ~\ref{table:workerTasks}.
 
-\begin{center}
 \begin{table}
@@
 \caption{Computation routines used by Sr workers}
+\label{table:workerTasks}
 \end{table}
-\end{center}
+
+The results of the word count job are then used in a script to compute the top 100 words.
+The cluster and word count job could be used in a two-stage top-k job.
+This script filters out SEO stopwords [stopword] to achieve more interesting results.
+
+\section{Evaluation}
+To evaluate Sr, I explore the speedup factor associated with varying the kill rate and target work level as well as the precision and recall of the word count test job.
+\subsection{Speedup}
+Sr is able to achieve a speedup over a MapReduce-style computation through three mechanisms: providing multiple computation routines for the workers to choose from; varying the task kill rate; and varying the target work level, which influences the chosen frequency of computation routines per worker.
+
+Table ~\ref{table:runtime} shows the effect of varying the kill rate and work level.
+The row with kill rate = 0.0 and work level = 1.0 represents the perfect, “correct” execution of the word count job.
+The only consistent reduction in execution time is a result of increasing the kill rate.
+Increasing the kill rate exhibits a linear reduction in execution time as the fraction of processed data linearly decreases.
+
+\begin{table}
+\begin{tabular}{|l|l|l|}
+\hline
+Kill rate & Work level & Avg. execution time \\ \hline
+0.0 & 1.0 & 11:35.5 \\ \hline
+0.0 & 0.4 & 10:33.8 \\ \hline
+0.0 & 0.8 & 10:30.8 \\ \hline
+0.2 & 0.4 & 08:25.8 \\ \hline
+0.2 & 0.8 & 08:37.8 \\ \hline
+0.4 & 0.4 & 06:54.0 \\ \hline
+0.4 & 0.8 & 06:28.2 \\ \hline
+0.6 & 0.4 & 04:14.7 \\ \hline
+0.6 & 0.8 & 04:13.7 \\ \hline
+0.8 & 0.4 & 02:33.3 \\ \hline
+0.8 & 0.8 & 02:15.0 \\ \hline
+\end{tabular}
+\caption{Impact of Kill rate and work level on job execution time}
+\label{table:runtime}
+\end{table}
+
+\subsection{Precision and Recall}
+In order for task killing to be an effective strategy for a top-k computation, the distribution of words in the corpus must be able to sustain data loss.
+This is the case if the distribution is long-tailed, but is not true if the distribution is uniform.
+
+\begin{figure}
+\includegraphics[width=\linewidth]{long-tail-ranks.png}
+\caption{Frequencies of words in the Wikipedia Featured Articles corpus}
+\label{fig:wordDist}
+\end{figure}
+
+The distribution shown in Figure ~\ref{fig:wordDist} is long-tailed, meaning that killing tasks will impact the tail of the distribution more than the head.
+
+\subsubsection{Precision}
+Task killing should least impact the head of the word distribution.
+Figure ~\ref{fig:precision} shows that even with a kill rate of 0.8 and a work level of 0.4, meaning that the cluster only looks at 8\% of the words in the corpus, the results are at least 80\% accurate.
+Increasing the work level, which increases the fidelity of results emitted by workers, also increases the fidelity of the top 100 results.
+
+\begin{figure}
+\includegraphics[width=\linewidth]{top-100-precision.png}
+\caption{Precision of top 100 results} 
+\label{fig:precision}
+\end{figure}
+
+\subsubsection{Test Accuracy}
+Because I am running a top k job, I compute the $F_{0.5}$-score of the Sr results as opposed to the $F1$-score because I care more about precision of the top k than recall in the tail.
+
+\section{Discussion}
+
+\section{Conclusion}
+
+\section{Acknowledgements}
+
+\section{References}
 

### 2012-05-03 paper/paper.tex
move some sections around

@@
 \section{Evaluation}
-To evaluate Sr, I explore the speedup factor associated with varying the kill rate and target work level as well as the precision and recall of the word count test job.
+To evaluate Sr, I explore the precision and recall of the word count test job as well as the speedup factor associated with varying the kill rate and target work level.
+
+\subsection{Precision and Recall}
+In order for task killing to be an effective strategy for a top-k computation, the distribution of words in the corpus must be able to sustain data loss.
+This is the case if the distribution is long-tailed, but is not true if the distribution is uniform.
+
+\begin{figure}
+\includegraphics[width=\linewidth]{long-tail-ranks.png}
+\caption{The frequencies of words in the Wikipedia Featured Articles corpus have a long-tailed distribution.}
+\label{fig:wordDist}
+\end{figure}
+
+The distribution shown in Figure ~\ref{fig:wordDist} is long-tailed, meaning that killing tasks will impact the tail of the distribution more than the head.
+
+\subsubsection{Precision}
+Task killing should least impact the head of the word distribution.
+Figure ~\ref{fig:precision} shows that even with a kill rate of 0.8 and a work level of 0.4, meaning that the cluster only looks at 8\% of the words in the corpus, the results are at least 80\% accurate.
+Increasing the work level, which increases the fidelity of results emitted by workers, also increases the fidelity of the top 100 results.
+
+\begin{figure}
+\includegraphics[width=\linewidth]{top-100-precision.png}
+\caption{Number of top 100 results returned in the top-100 by the word count job}
+\label{fig:precision}
+\end{figure}
+
+\subsubsection{Word Count Job Accuracy}
+Because I am running a top-k job, I compute the $F_{0.5}$-score of the Sr results as opposed to the $F1$-score because I care more about precision of the top k than recall in the tail.
+Figure ~\ref{fig:fscore} shows that the $F_{0.5}$-score, or the weighted accuracy of the top-100 classifier, is always higher than the fraction of the input examined (kill rate * work level).
+
+\begin{figure}
+\includegraphics[width=\linewidth]{f-score.png}
+\caption{$F_{0.5}$-score for the top-100 word count job.
+I measured the $F$-score with $\beta = 0.5$ because the goal of the job is to run a top-k filter on it, meaning I care more about precision than recall.}
+\label{fig:fscore}
+\end{figure}
+
 \subsection{Speedup}
@@
 Table ~\ref{table:runtime} shows the effect of varying the kill rate and work level.
-The row with kill rate = 0.0 and work level = 1.0 represents the perfect, “correct” execution of the word count job.
+The row with kill rate = 0.0 and work level = 1.0 represents the perfect, MapReduce-style, execution of the word count job.
 The only consistent reduction in execution time is a result of increasing the kill rate.
@@
 
-\subsection{Precision and Recall}
-In order for task killing to be an effective strategy for a top-k computation, the distribution of words in the corpus must be able to sustain data loss.
-This is the case if the distribution is long-tailed, but is not true if the distribution is uniform.
-
-\begin{figure}
-\includegraphics[width=\linewidth]{long-tail-ranks.png}
-\caption{Frequencies of words in the Wikipedia Featured Articles corpus}
-\label{fig:wordDist}
-\end{figure}
-
-The distribution shown in Figure ~\ref{fig:wordDist} is long-tailed, meaning that killing tasks will impact the tail of the distribution more than the head.
-
-\subsubsection{Precision}
-Task killing should least impact the head of the word distribution.
-Figure ~\ref{fig:precision} shows that even with a kill rate of 0.8 and a work level of 0.4, meaning that the cluster only looks at 8\% of the words in the corpus, the results are at least 80\% accurate.
-Increasing the work level, which increases the fidelity of results emitted by workers, also increases the fidelity of the top 100 results.
-
-\begin{figure}
-\includegraphics[width=\linewidth]{top-100-precision.png}
-\caption{Precision of top 100 results} 
-\label{fig:precision}
-\end{figure}
-
-\subsubsection{Test Accuracy}
-Because I am running a top k job, I compute the $F_{0.5}$-score of the Sr results as opposed to the $F1$-score because I care more about precision of the top k than recall in the tail.
+Notably, simply by killing tasks, Sr is able to achieve over a 5 times speedup compared to the perfect execution while still returning about 84 of the top-100 words.
 

### 2012-05-03 paper/paper.tex
Baller tables

@@
 \graphicspath{{images/}}
+\usepackage{tabularx}
 
@@
 \begin{table}
-\begin{tabular}{|l|p{5cm}|}
+\begin{tabularx}{\linewidth}{|c|X|}
  \hline
@@
 0.1 & Return the results of the last computation from a cache \\ \hline
-\end{tabular}
+\end{tabularx}
 \caption{Computation routines used by Sr workers}
@@
 Figure ~\ref{fig:fscore} shows that the $F_{0.5}$-score, or the weighted accuracy of the top-100 classifier, is always higher than the fraction of the input examined (kill rate * work level).
+Setting the work level to 0.4 nets a greater increase in job accuracy versus fraction of words examined, with accuracy approximately 1.75 times more than the fraction of words examined.
 
@@
 \begin{table}
-\begin{tabular}{|l|l|l|}
+\begin{tabularx}{\linewidth}{|X|X|X|}
 \hline
-Kill rate & Work level & Avg. execution time \\ \hline
+Kill rate & Work level & Avg. execution time [minutes] \\ \hline
 0.0 & 1.0 & 11:35.5 \\ \hline
@@
 0.8 & 0.8 & 02:15.0 \\ \hline
-\end{tabular}
-\caption{Impact of Kill rate and work level on job execution time}
+\end{tabularx}
+\caption{Impact of kill rate and work level on job execution time.}
 \label{table:runtime}
@@
 
-\section{Discussion}
-
-\section{Conclusion}
-
-\section{Acknowledgements}
-
-\section{References}
-
 \end{document}

### 2012-05-04 paper/paper.tex
Add introduction

@@
 \section{Introduction}
+\label{sec:intro}
+One of the fundamental problems MapReduce was created to solve was processing the growing amount of data in the world.
+Now with the open source Apache Hadoop and Pig, it is easy to process and query the terabytes of data an organization may collect.
+With terabytes of data, however, it is scarcely necessary to examine every entry to uncover trends.
+Google runs PageRank on the entire Internet, but if it only did on half of the pages it crawls, it would likely still have a usable index for delivering the first 5 pages of results.
+
+How does one decide which data to process then?
+Selctively deciding which data to log is problematic because it can systemically mask some of the trends one would try to uncover through analysis.
+In this paper, I explore the possibility of discarding data randomly and choosing to process the data I do see at differing fidelities in order to save work.
+
+One of the problems with MapReduce that Google has solved with Caffeine is how to incorporate new data into an already analyzed task.
+MapReduce simply says to rerun the job with the new data included.
+Others have solved this problem by batching data into chunks and continuously spawning MapReduce jobs to incorporate the new data.
+
+A simpler way to incorporate new data is to treat data not as a constant, but as a stream.
+By processing data on demand, one avoids repeating work, can save resources by spinning workers up and down as necessary, and ensure results are as fresh as possible.
+
+The remainder of this paper is organized as follows.
+Section ~\ref{sec:relwork} provides an overview of related work on distributed stream processing as well as dynamic and approximate computations.
+Section ~\ref{sec:design} details how I designed Sr.
+Section ~\ref{sec:methodology} explains the methodology used to perform a cvase study using Sr.
+Section ~\ref{sec:evaluation} evaluates the effectiveness of Sr in the case study.
 
 \section{Related Work}
+\label{sec:relwork}
 
 \section{Design}
+\label{sec:design}
 Sr is a distributed system for processing streams that can choose to kill tasks or limit the amount of work it performs per task.
@@
 I decided to make use of a library [Sinatra.rb] providing the server functionality because there was a low barrier to getting inter-node communication functioning.
-This design choice presents some problems and will be discussed further in section 5.
+This design choice presents some problems and will be discussed further in Section ~\ref{sec:discussion}.
 
@@
 \section{Methodology}
+\label{sec:methodology}
 The cluster I used to test Sr is a 5-node network consisting of 1 spout, 1 fetcher, 4 workers, 1 collector, and 1 master.
@@
 \section{Evaluation}
+\label{sec:evaluation}
 To evaluate Sr, I explore the precision and recall of the word count test job as well as the speedup factor associated with varying the kill rate and target work level.

### 2012-05-04 paper/paper.tex
Tilde thing for refs

@@
 The remainder of this paper is organized as follows.
-Section ~\ref{sec:relwork} provides an overview of related work on distributed stream processing as well as dynamic and approximate computations.
-Section ~\ref{sec:design} details how I designed Sr.
-Section ~\ref{sec:methodology} explains the methodology used to perform a cvase study using Sr.
-Section ~\ref{sec:evaluation} evaluates the effectiveness of Sr in the case study.
+Section~\ref{sec:relwork} provides an overview of related work on distributed stream processing as well as dynamic and approximate computations.
+Section~\ref{sec:design} details how I designed Sr.
+Section~\ref{sec:methodology} explains the methodology used to perform a cvase study using Sr.
+Section~\ref{sec:evaluation} evaluates the effectiveness of Sr in the case study.
 
@@
 I decided to make use of a library [Sinatra.rb] providing the server functionality because there was a low barrier to getting inter-node communication functioning.
-This design choice presents some problems and will be discussed further in Section ~\ref{sec:discussion}.
+This design choice presents some problems and will be discussed further in Section~\ref{sec:discussion}.
 
@@
 The cluster I used to test Sr is a 5-node network consisting of 1 spout, 1 fetcher, 4 workers, 1 collector, and 1 master.
-Roles are partitioned among nodes as shown in Figure ~\ref{fig:clusterDiagram}.
+Roles are partitioned among nodes as shown in Figure~\ref{fig:clusterDiagram}.
 Worker nodes were XVM [SIPB] VMs provisioned with 128MB RAM each.
@@
 
-Workers are initialized with the 3 computation routines shown in Table ~\ref{table:workerTasks}.
+Workers are initialized with the 3 computation routines shown in Table~\ref{table:workerTasks}.
 
@@
 
-The distribution shown in Figure ~\ref{fig:wordDist} is long-tailed, meaning that killing tasks will impact the tail of the distribution more than the head.
+The distribution shown in Figure~\ref{fig:wordDist} is long-tailed, meaning that killing tasks will impact the tail of the distribution more than the head.
 
@@
 Task killing should least impact the head of the word distribution.
-Figure ~\ref{fig:precision} shows that even with a kill rate of 0.8 and a work level of 0.4, meaning that the cluster only looks at 8\% of the words in the corpus, the results are at least 80\% accurate.
+Figure~\ref{fig:precision} shows that even with a kill rate of 0.8 and a work level of 0.4, meaning that the cluster only looks at 8\% of the words in the corpus, the results are at least 80\% accurate.
 Increasing the work level, which increases the fidelity of results emitted by workers, also increases the fidelity of the top 100 results.
@@
 Because I am running a top-k job, I compute the $F_{0.5}$-score of the Sr results as opposed to the $F1$-score because I care more about precision of the top k than recall in the tail.
-Figure ~\ref{fig:fscore} shows that the $F_{0.5}$-score, or the weighted accuracy of the top-100 classifier, is always higher than the fraction of the input examined (kill rate * work level).
+Figure~\ref{fig:fscore} shows that the $F_{0.5}$-score, or the weighted accuracy of the top-100 classifier, is always higher than the fraction of the input examined (kill rate * work level).
 Setting the work level to 0.4 nets a greater increase in job accuracy versus fraction of words examined, with accuracy approximately 1.75 times more than the fraction of words examined.
@@
 
-Table ~\ref{table:runtime} shows the effect of varying the kill rate and work level.
+Table~\ref{table:runtime} shows the effect of varying the kill rate and work level.
 The row with kill rate = 0.0 and work level = 1.0 represents the perfect, MapReduce-style, execution of the word count job.

### 2012-05-04 paper/paper.tex
Hard wrap lines in tex source

@@
 
-\title{Sr: Processing Data Streams By Doing Less Work}
+\title{Sr: Processing Data Streams and Avoiding Work}
 \author{Ryan Lopopolo\\
@@
 \label{sec:intro}
-One of the fundamental problems MapReduce was created to solve was processing the growing amount of data in the world.
-Now with the open source Apache Hadoop and Pig, it is easy to process and query the terabytes of data an organization may collect.
-With terabytes of data, however, it is scarcely necessary to examine every entry to uncover trends.
-Google runs PageRank on the entire Internet, but if it only did on half of the pages it crawls, it would likely still have a usable index for delivering the first 5 pages of results.
+One of the fundamental problems MapReduce was created to solve was processing
+the growing amount of data in the world. Now with the open source Apache Hadoop
+and Pig, it is easy to process and query the terabytes of data an organization
+may collect. With terabytes of data, however, it is scarcely necessary to examine
+every entry to uncover trends. Google runs PageRank on the entire Internet, but if
+it only did on half of the pages it crawls, it would likely still have a usable
+index for delivering the first 5 pages of results.
 
-How does one decide which data to process then?
-Selctively deciding which data to log is problematic because it can systemically mask some of the trends one would try to uncover through analysis.
-In this paper, I explore the possibility of discarding data randomly and choosing to process the data I do see at differing fidelities in order to save work.
+How does one decide which data to process then? Selctively deciding which data to
+log is problematic because it can systemically mask some of the trends one would
+try to uncover through analysis. In this paper, I explore the possibility of
+discarding data randomly and choosing to process the data I do see at differing
+fidelities in order to save work.
 
-One of the problems with MapReduce that Google has solved with Caffeine is how to incorporate new data into an already analyzed task.
-MapReduce simply says to rerun the job with the new data included.
-Others have solved this problem by batching data into chunks and continuously spawning MapReduce jobs to incorporate the new data.
+One of the problems with MapReduce that Google has solved with Caffeine is how to
+incorporate new data into an already analyzed task. MapReduce simply says to rerun
+the job with the new data included. Others have solved this problem by batching data
+into chunks and continuously spawning MapReduce jobs to incorporate the new data.
 
-A simpler way to incorporate new data is to treat data not as a constant, but as a stream.
-By processing data on demand, one avoids repeating work, can save resources by spinning workers up and down as necessary, and ensure results are as fresh as possible.
+A simpler way to incorporate new data is to treat data not as a constant, but as a
+stream. By processing data on demand, one avoids repeating work, can save resources
+by spinning workers up and down as necessary, and ensure results are as fresh as possible.
 
-The remainder of this paper is organized as follows.
-Section~\ref{sec:relwork} provides an overview of related work on distributed stream processing as well as dynamic and approximate computations.
-Section~\ref{sec:design} details how I designed Sr.
-Section~\ref{sec:methodology} explains the methodology used to perform a cvase study using Sr.
-Section~\ref{sec:evaluation} evaluates the effectiveness of Sr in the case study.
+The remainder of this paper is organized as follows. Section~\ref{sec:relwork} provides
+an overview of related work on distributed stream processing as well as dynamic and
+approximate computations. Section~\ref{sec:design} details how I designed Sr.
+Section~\ref{sec:methodology} explains the methodology used to perform a cvase study
+using Sr. Section~\ref{sec:evaluation} evaluates the effectiveness of Sr in the case study.
 
@@
 \label{sec:design}
-Sr is a distributed system for processing streams that can choose to kill tasks or limit the amount of work it performs per task.
-Its design is modular; there are five different types of nodes in an Sr cluster (spout, fetcher, worker, collector, master).
+Sr is a distributed system for processing streams that can choose to kill tasks or
+limit the amount of work it performs per task. Its design is modular; there are five
+different types of nodes in an Sr cluster (spout, fetcher, worker, collector, master).
 \subsection{Spout}
 Spouts are network-connected machines that generate data for the Sr cluster to process.
-Examples include a machine that tails a log file or an API like the Twitter tweet stream.
-Fetchers depend on spouts as a source of streaming data.
+Examples include a machine that tails a log file or an API like the Twitter tweet
+stream. Fetchers depend on spouts as a source of streaming data.
 \subsection{Fetcher}
-Fetchers are responsible for communicating with spouts and returning data for the workers to process. Fetchers may run indefinitely or return a status code indicating the fetching task is over.
+Fetchers are responsible for communicating with spouts and returning data for the
+workers to process. Fetchers may run indefinitely or return a status code indicating
+the fetching task is over.
 \subsection{Worker}
-Workers perform processing on data provided by fetchers.
-They are similar to mappers in the MapReduce framework.
-Each worker receives a fraction of the total input data and each worker’s tasks are independent of other workers’.
+Workers perform processing on data provided by fetchers. They are similar to mappers
+in the MapReduce framework. Each worker receives a fraction of the total input data
+and each worker’s tasks are independent of other workers’.
 
-Workers are responsible for fulfilling the main design goals of Sr.
-Workers may choose to kill a task preemptively or if it does not complete before a timeout.
-Additionally, workers may choose among a variety of routines for performing computation on a datum.
-Routines are ranked on a [0,1] scale based on the estimated fraction of total work it requires.
+Workers are responsible for fulfilling the main design goals of Sr. Workers may choose
+to kill a task preemptively or if it does not complete before a timeout. Additionally,
+workers may choose among a variety of routines for performing computation on a datum.
+Routines are ranked on a [0,1] scale based on the estimated fraction of total work it
+requires.
 
-As it runs, a worker maintains an internal metric that estimates the fraction of work it has performed over all data it has seen.
-Workers use this metric when choosing which computation routine to run for a datum.
-A worker will choose the lowest ranked routine such that its estimated fraction of work is above a configured threshold.
+As it runs, a worker maintains an internal metric that estimates the fraction of work
+it has performed over all data it has seen. Workers use this metric when choosing which
+computation routine to run for a datum. A worker will choose the lowest ranked routine
+such that its estimated fraction of work is above a configured threshold.
 
-Because one of Sr’s goals is to process (potentially infinite) streams, workers do not save their progress to disk and are forgetful; once the master queries a worker for its progress and the worker successfully returns it, the worker clears all of its state and continues processing.
-As a consequence, workers are easy to add or remove from the worker pool because they don’t need to be initialized with long-term job state.
-Additionally, as long as the master polls workers frequently enough, when a worker fails, only a small fraction of the total work is lost.
-The master queries workers every 100ms by default.
+Because one of Sr’s goals is to process (potentially infinite) streams, workers do not
+save their progress to disk and are forgetful; once the master queries a worker for its
+progress and the worker successfully returns it, the worker clears all of its state and
+continues processing. As a consequence, workers are easy to add or remove from the worker
+pool because they don’t need to be initialized with long-term job state. Additionally, as
+long as the master polls workers frequently enough, when a worker fails, only a small
+fraction of the total work is lost. The master queries workers every 100ms by default.
 \subsection{Collector}
-Collector nodes aggregate the results of all workers.
-Each collector acts as a reducer in the MapReduce framework if MapReduce used a single reducer for all of the mappers.
-Collectors differ from MapReduce reducers in that they receive their data piecewise, as it is produced from workers as opposed to after all mappers have completed.
-This limits the type of aggregation collectors can do to online operations.
+Collector nodes aggregate the results of all workers. Each collector acts as a reducer
+in the MapReduce framework if MapReduce used a single reducer for all of the mappers.
+Collectors differ from MapReduce reducers in that they receive their data piecewise, as it
+is produced from workers as opposed to after all mappers have completed. This limits the
+type of aggregation collectors can do to online operations.
 
-Collectors also expose an API endpoint for accessing the results of a job. This endpoint can be used by another spout to chain Sr jobs together.
+Collectors also expose an API endpoint for accessing the results of a job. This endpoint
+can be used by another spout to chain Sr jobs together.
 \subsection{Master}
-There is one master node per Sr network.
-It has a function similar to the jobtracker in MapReduce.
-New jobs are scheduled with the master and it initializes other nodes in the cluster with job state.
-For each job, the master schedules roles among nodes in a round robin manner to minimize the total number of outstanding roles on any one node.
+There is one master node per Sr network. It has a function similar to the jobtracker in
+MapReduce. New jobs are scheduled with the master and it initializes other nodes in the
+cluster with job state. For each job, the master schedules roles among nodes in a round robin
+manner to minimize the total number of outstanding roles on any one node.
 
-The master is the only well-known node in the cluster.
-Other nodes in the network exclusively communicate with the master.
-The master and other nodes communicate with each other by issuing HTTP requests to a simple server on each node.
-I decided to make use of a library [Sinatra.rb] providing the server functionality because there was a low barrier to getting inter-node communication functioning.
-This design choice presents some problems and will be discussed further in Section~\ref{sec:discussion}.
+The master is the only well-known node in the cluster. Other nodes in the network exclusively
+communicate with the master. The master and other nodes communicate with each other by issuing
+HTTP requests to a simple server on each node. I decided to make use of a library [Sinatra.rb]
+providing the server functionality because there was a low barrier to getting inter-node
+communication functioning. This design choice presents some problems and will be discussed
+further in Section~\ref{sec:discussion}.
 
-Another consequence of the master being the only well-known node is that all data in the cluster must flow through it.
-The master maintains two queues per job for buffering job progress from fetchers and workers and periodically pushes this state out to workers and collectors, respectively.
+Another consequence of the master being the only well-known node is that all data in the
+cluster must flow through it. The master maintains two queues per job for buffering job
+progress from fetchers and workers and periodically pushes this state out to workers and
+collectors, respectively.
 \subsection{Configuring a Cluster for a Job}
-Apart from spouts, all nodes in a cluster modify their behavior based on the job they are running.
-The master must know the appropriate number of nodes to spin up; fetchers need to know how to talk to spouts; workers need to know how to compute results; and collectors need to know how to combine batched worker results.
+Apart from spouts, all nodes in a cluster modify their behavior based on the job they are
+running. The master must know the appropriate number of nodes to spin up; fetchers need to
+know how to talk to spouts; workers need to know how to compute results; and collectors need
+to know how to combine batched worker results.
 
-Sr accomplishes this configuration with a Jobfile.
-Jobfiles are instances of a special class provided by the Sr framework.
-This class exposes several methods that can be invoked by a given node to provide configuration parameters or execute code on its behalf.
-Most of the routines that advance the progress of an Sr job are wrappers around these Jobfile methods.
+Sr accomplishes this configuration with a Jobfile. Jobfiles are instances of a special class
+provided by the Sr framework. This class exposes several methods that can be invoked by a
+given node to provide configuration parameters or execute code on its behalf. Most of the
+routines that advance the progress of an Sr job are wrappers around these Jobfile methods.
 
-Sr sends the source of the Jobfile to every node participating in the job and uses eval to obtain a local instance of the Jobfile class. An example jobfile can be found at [github].
+Sr sends the source of the Jobfile to every node participating in the job and uses eval to
+obtain a local instance of the Jobfile class. An example jobfile can be found at [github].
 
-The use of eval to instantiate Jobfile objects and the implementation language’s (Ruby) ability to monkeypatch classes means that jobs can be modified on the fly just by sending an updated Jobfile to job participants.
-For example, a job can be made lower fidelity in the face of an impending time constraint or higher fidelity if more workers are added to the cluster.
+The use of eval to instantiate Jobfile objects and the implementation language’s (Ruby)
+ability to monkeypatch classes means that jobs can be modified on the fly just by sending
+an updated Jobfile to job participants. For example, a job can be made lower fidelity in
+the face of an impending time constraint or higher fidelity if more workers are added to
+the cluster.
 \subsection{Fault Tolerance}
-Sr can sustain the failure of any node other than the master.
-Because the master is responsible for shuffling data between fetchers, workers, and collectors, a job cannot make progress without the master.
+Sr can sustain the failure of any node other than the master. Because the master is responsible
+for shuffling data between fetchers, workers, and collectors, a job cannot make progress without
+the master.
 
-Fetchers can fail.
-The only consequence of fetcher failure is that some of the input stream is lost forever.
-Since streams contain much data and are likely stored permanently elsewhere on disk, Sr does not attempt to recover this data.
+Fetchers can fail. The only consequence of fetcher failure is that some of the input stream is
+lost forever. Since streams contain much data and are likely stored permanently elsewhere on disk
+Sr does not attempt to recover this data.
 
-Worker failures may entail some lost work.
-Having the master poll each worker frequently for its progress mitigates the consequences of worker failure.
-For jobs that run for minutes or hours, 100ms of lost work is << 0.1% of the total.
-Sr can simply treat these lost tasks as preemptively killed, which is already expected by the cluster.
+Worker failures may entail some lost work. Having the master poll each worker frequently for its
+progress mitigates the consequences of worker failure. For jobs that run for minutes or hours,
+100ms of lost work is << 0.1\% of the total. Sr can simply treat these lost tasks as preemptively
+killed, which is already expected by the cluster.
 
-Each collector is an exact replica of all others. Collector failure does not impact correctness of the results delivered by any other collector.
+Each collector is an exact replica of all others. Collector failure does not impact correctness of
+the results delivered by any other collector.
 \subsection{Killing Tasks and Working Less}
-A design goal of Sr is to compute meaningful results from a stream and to do so while not processing every datum one-to-one.
-Sr achieves this goal in two different ways.
-First, workers may kill tasks preemptively to avoid the time and resource costs associated with processing that task.
-Second, workers rely on the Jobfile to provide them with several different computation routines of differing fidelities that perform a fraction of the total work on a datum.
+A design goal of Sr is to compute meaningful results from a stream and to do so while not
+processing every datum one-to-one. Sr achieves this goal in two different ways. First, workers
+may kill tasks preemptively to avoid the time and resource costs associated with processing
+that task. Second, workers rely on the Jobfile to provide them with several different
+computation routines of differing fidelities that perform a fraction of the total work on a
+datum.
 
-These behaviors appeal to the law of large numbers.
-It assumes that trends will still be visible in spite of looking at only a fraction of the data.
-This means that the computation routines and the weights assigned to them must be adapted to fit the distribution of the data before the job starts (or updated in situ via a new Jobfile).
+These behaviors appeal to the law of large numbers. It assumes that trends will still be
+visible in spite of looking at only a fraction of the data. This means that the computation
+routines and the weights assigned to them must be adapted to fit the distribution of the data
+before the job starts (or updated in situ via a new Jobfile).
 
@@
 \label{sec:methodology}
-The cluster I used to test Sr is a 5-node network consisting of 1 spout, 1 fetcher, 4 workers, 1 collector, and 1 master.
-Roles are partitioned among nodes as shown in Figure~\ref{fig:clusterDiagram}.
-Worker nodes were XVM [SIPB] VMs provisioned with 128MB RAM each.
+The cluster I used to test Sr is a 5-node network consisting of 1 spout, 1 fetcher, 4 workers,
+1 collector, and 1 master. Roles are partitioned among nodes as shown in
+Figure~\ref{fig:clusterDiagram}. Worker nodes were XVM [SIPB] VMs provisioned with 128MB RAM each.
 The master, spout, fetcher, and collector ran on my laptop, a mid-2010 Macbook Air with 4GB of RAM.
@@
                   |--------|
-
 \end{verbatim}
-\caption{Topology of the test Sr cluster. Each box is a single machine.}
+\caption{Topology of the test Sr cluster used in the word count case study.\\
+Each box is a single machine.}
 \label{fig:clusterDiagram}
@@
 
-The job I ran was a word counter. The collector emits a hash whose keys are words and whose values are the frequency that word has occurred in the test corpus.
+The job I ran was a word counter. The collector emits a hash whose keys are words and whose
+values are the frequency that word has occurred in the test corpus.
 
-To run the job, I had to create a spout and find a source of data.
-For data, I acquired a Wikipedia dump of the Featured Articles category.
-I used Wikipedia’s xml exporter [Special:export] on January 9, 2012.
+To run the job, I had to create a spout and find a source of data. For data, I acquired a
+Wikipedia dump of the Featured Articles category. I used Wikipedia’s xml exporter
+[Special:export] on January 9, 2012.
 
-To serve the data, I munged it into a YAML file containing a hash of \lstinline[language=Ruby]{article_id : fulltext}.
-To store fulltext, I base64 encoded it and deflated it.
-This requires workers to inflate and decode the fulltext before they can process it further.
-The server reads from this YAML file and returns the resulting hash as JSON.
+To serve the data, I munged it into a YAML file containing a hash of
+\lstinline[language=Ruby]{article_id : fulltext}. To store fulltext, I base64 encoded it and
+deflated it using zlib. This requires workers to inflate and decode the fulltext before they
+can process it further. The server reads from this YAML file and returns the resulting hash as
+JSON.
 
-The fetcher communicates to the spout by requesting sequential article ids until it has fetched every article.
+The fetcher communicates to the spout by requesting sequential article ids until it has fetched
+every article.
 
@@
 The results of the word count job are then used in a script to compute the top 100 words.
-The cluster and word count job could be used in a two-stage top-k job.
-This script filters out SEO stopwords [stopword] to achieve more interesting results.
+The cluster and word count job could be used in a two-stage top-k job. This script filters
+out SEO stopwords [stopword] to achieve more interesting results.
 
@@
 \label{sec:evaluation}
-To evaluate Sr, I explore the precision and recall of the word count test job as well as the speedup factor associated with varying the kill rate and target work level.
+To evaluate Sr, I explore the precision and recall of the word count test job as well as the
+speedup factor associated with varying the kill rate and target work level.
 
 \subsection{Precision and Recall}
-In order for task killing to be an effective strategy for a top-k computation, the distribution of words in the corpus must be able to sustain data loss.
-This is the case if the distribution is long-tailed, but is not true if the distribution is uniform.
+In order for task killing to be an effective strategy for a top-k computation, the
+distribution of words in the corpus must be able to sustain data loss. This is the case
+if the distribution is long-tailed, but is not true if the distribution is uniform.
 
@@
 \includegraphics[width=\linewidth]{long-tail-ranks.png}
-\caption{The frequencies of words in the Wikipedia Featured Articles corpus have a long-tailed distribution.}
+\caption{The frequencies of words in the Wikipedia Featured Articles corpus\\
+have a long-tailed distribution.}
 \label{fig:wordDist}
@@
 
-The distribution shown in Figure~\ref{fig:wordDist} is long-tailed, meaning that killing tasks will impact the tail of the distribution more than the head.
+The distribution shown in Figure~\ref{fig:wordDist} is long-tailed, meaning that killing
+tasks will impact the tail of the distribution more than the head.
 
@@
 Task killing should least impact the head of the word distribution.
-Figure~\ref{fig:precision} shows that even with a kill rate of 0.8 and a work level of 0.4, meaning that the cluster only looks at 8\% of the words in the corpus, the results are at least 80\% accurate.
-Increasing the work level, which increases the fidelity of results emitted by workers, also increases the fidelity of the top 100 results.
+Figure~\ref{fig:precision} shows that even with a kill rate of 0.8 and a work level of
+0.4, meaning that the cluster only looks at 8\% of the words in the corpus, the results
+are at least 80\% accurate. Increasing the work level, which increases the fidelity of
+results emitted by workers, also increases the fidelity of the top 100 results.
 
@@
 \subsubsection{Word Count Job Accuracy}
-Because I am running a top-k job, I compute the $F_{0.5}$-score of the Sr results as opposed to the $F1$-score because I care more about precision of the top k than recall in the tail.
-Figure~\ref{fig:fscore} shows that the $F_{0.5}$-score, or the weighted accuracy of the top-100 classifier, is always higher than the fraction of the input examined (kill rate * work level).
-Setting the work level to 0.4 nets a greater increase in job accuracy versus fraction of words examined, with accuracy approximately 1.75 times more than the fraction of words examined.
+Because I am running a top-k job, I compute the $F_{0.5}$-score of the Sr results as
+opposed to the $F1$-score because I care more about precision of the top k than recall
+in the tail. Figure~\ref{fig:fscore} shows that the $F_{0.5}$-score, or the weighted
+accuracy of the top-100 classifier, is always higher than the fraction of the input
+examined (kill rate * work level). Setting the work level to 0.4 nets a greater increase
+in job accuracy versus fraction of words examined, with accuracy approximately 1.75 times
+more than the fraction of words examined.
 
@@
 \includegraphics[width=\linewidth]{f-score.png}
-\caption{$F_{0.5}$-score for the top-100 word count job.
-I measured the $F$-score with $\beta = 0.5$ because the goal of the job is to run a top-k filter on it, meaning I care more about precision than recall.}
+\caption{$F_{0.5}$-score for the top-100 word count job. I measured the $F$-score with\\
+$\beta=0.5$ because the goal of the job is to run a top-k filter on it, meaning I care more\\
+about precision than recall.}
 \label{fig:fscore}
@@
 \subsection{Speedup}
-Sr is able to achieve a speedup over a MapReduce-style computation through three mechanisms: providing multiple computation routines for the workers to choose from; varying the task kill rate; and varying the target work level, which influences the chosen frequency of computation routines per worker.
+Sr is able to achieve a speedup over a MapReduce-style computation through three mechanisms:
+providing multiple computation routines for the workers to choose from; varying the task kill
+rate; and varying the target work level, which influences the chosen frequency of computation
+routines per worker.
 
-Table~\ref{table:runtime} shows the effect of varying the kill rate and work level.
-The row with kill rate = 0.0 and work level = 1.0 represents the perfect, MapReduce-style, execution of the word count job.
-The only consistent reduction in execution time is a result of increasing the kill rate.
-Increasing the kill rate exhibits a linear reduction in execution time as the fraction of processed data linearly decreases.
+Table~\ref{table:runtime} shows the effect of varying the kill rate and work level. The row
+with kill~rate~=~0.0 and work~level~=~1.0 represents the perfect, MapReduce-style, execution
+of the word count job. The only consistent reduction in execution time is a result of
+increasing the kill rate. Increasing the kill rate exhibits a linear reduction in execution
+time as the fraction of processed data linearly decreases.
 
@@
 \hline
-Kill rate & Work level & Avg. execution time [minutes] \\ \hline
+Kill rate & Work level & Average execution time [minutes] \\ \hline
 0.0 & 1.0 & 11:35.5 \\ \hline
@@
 
-Notably, simply by killing tasks, Sr is able to achieve over a 5 times speedup compared to the perfect execution while still returning about 84 of the top-100 words.
+Notably, simply by killing tasks, Sr is able to achieve over a 5 times speedup compared
+to the perfect execution while still returning about 84 of the top-100 words.
 

### 2012-05-04 paper/paper.tex
Unbreak captions

@@
 \end{verbatim}
-\caption{Topology of the test Sr cluster used in the word count case study.\\
-Each box is a single machine.}
+\caption{Topology of the test Sr cluster used in the word count case study. Each box is a single machine.}
 \label{fig:clusterDiagram}
@@
 \includegraphics[width=\linewidth]{long-tail-ranks.png}
-\caption{The frequencies of words in the Wikipedia Featured Articles corpus\\
-have a long-tailed distribution.}
+\caption{The frequencies of words in the Wikipedia Featured Articles corpus have a long-tailed distribution.}
 \label{fig:wordDist}
@@
 \includegraphics[width=\linewidth]{top-100-precision.png}
-\caption{Number of top 100 results returned in the top-100 by the word count job}
+\caption{Number of top 100 results returned in the top-100 by the word count job.}
 \label{fig:precision}
@@
 \includegraphics[width=\linewidth]{f-score.png}
-\caption{$F_{0.5}$-score for the top-100 word count job. I measured the $F$-score with\\
-$\beta=0.5$ because the goal of the job is to run a top-k filter on it, meaning I care more\\
-about precision than recall.}
+\caption{$F_{0.5}$-score for the top-100 word count job.
+I measured the $F$-score with $\beta=0.5$ because the goal of the job is to run a top-k filter on it, meaning I care more about precision than recall.}
 \label{fig:fscore}
@@
 
+\section{Discussion}
+\label{sec:discussion}
+
+\bibliography{sr}{}
+\bibliographystyle{plain}
+
 \end{document}

### 2012-05-04 paper/paper.tex
Add discussion section

@@
 \usepackage{tabularx}
+\usepackage{url}
 
@@
 the growing amount of data in the world. Now with the open source Apache Hadoop
-and Pig, it is easy to process and query the terabytes of data an organization
+and Pig~\cite{piglatin}, it is easy to process and query the terabytes of data an organization
 may collect. With terabytes of data, however, it is scarcely necessary to examine
@@
 using Sr. Section~\ref{sec:evaluation} evaluates the effectiveness of Sr in the case study.
+Section~\ref{sec:discussion} enumerates issues with Sr's current implementation.
 
@@
 \subsection{Master}
+\label{sec:master}
 There is one master node per Sr network. It has a function similar to the jobtracker in
@@
 \subsection{Configuring a Cluster for a Job}
+\label{sec:jobfile}
 Apart from spouts, all nodes in a cluster modify their behavior based on the job they are
@@
 The cluster and word count job could be used in a two-stage top-k job. This script filters
-out SEO stopwords [stopword] to achieve more interesting results.
+out SEO stopwords~\cite{stopwords} to achieve more interesting results.
 
@@
 
-\section{Discussion}
+\section{Implementation Notes}
 \label{sec:discussion}
+This section describes deficiencies in the implementation of Sr used to run the case study
+in this paper and goals for the next version of the system.
 
-\bibliography{sr}{}
+\subsection{On-the-Fly Job Reconfiguration}
+The mechanism for altering execution of a job as it is running described in Section~\ref{sec:jobfile}
+is not yet implemented. Adding this feature to Sr is a matter of adding an API endpoint
+to the servers run by each role and adding a bin-script to submit the new Jobfile.
+
+\subsection{Internode Communication}
+In Section~\ref{sec:master} I mentioned design difficulties relating to the master and using HTTP
+servers for sending messages between nodes. I initially chose to use HTTP requests with POST payloads
+to send data and results between nodes because of its low barrier to entry; however, initiating many
+HTTP requests in succession is expensive. When killing jobs on worker nodes, the observed time savings
+was minimal because most of the time spent per datum involved shipping it from the master to the worker.
+
+In order to mitigate the effects of this problem, I batched individual requests into groups of 5. This
+lowered the number of connections I was initiating but it also limited the parallelism of the cluster
+and removed workers from the pool for longer periods because they had more data to process at a time.
+A killed task on the worker no longer freed it up to receive a new task immediately.
+Keeping workers removed from the pool caused the queues on the master to grow longer as the workers
+could no longer keep up with the rate the fetcher was producing data.
+
+Eventually, I introduced a configuration option to kill tasks at the master. The master then
+decides to discard a task as it is popped from the queue, before it is ever sent to a worker.
+Doing so improved the execution time of the cluster but also meant that workers no longer had
+a full idea of how accurate they were being because they never killed any tasks themselves.
+
+In order to address this problem, the master needs to keep a persistent channel open between
+it and all active nodes. Communication channels should be established when nodes come online.
+Possible solutions include writing to a socket or using a higher abstraction like AMPQ. AMPQ
+is appealing because it relieves the master from handling queues.
+
+\subsection{Node Health}
+Currently, the master does not probe nodes to ensure that they are responsive. In the case that
+a node is serving a worker role for a job, this deficiency is masked. The node will simply not
+return the HTTP request sent to it to push it some data and the worker will remain removed from
+the pool. If the node is in the role of fetcher or collector, the master will stall.
+
+All messages passed by the master to other nodes must be made non-blocking.
+
+\subsection{Job Management}
+There is no support for killing jobs or removing them from the master's data structures. The only
+way to remove a job is to kill the master and all other nodes in the cluster.
+
+\bibliography{paper}{}
 \bibliographystyle{plain}

### 2012-05-04 paper/paper.tex
Formatting the hash code
more citations

@@
 may collect. With terabytes of data, however, it is scarcely necessary to examine
-every entry to uncover trends. Google runs PageRank on the entire Internet, but if
+every entry to uncover trends, especially when one only cares about the most prominent
+trends or results. Google runs PageRank on the entire Internet, but if
 it only did on half of the pages it crawls, it would likely still have a usable
@@
 try to uncover through analysis. In this paper, I explore the possibility of
-discarding data randomly and choosing to process the data I do see at differing
-fidelities in order to save work.
+discarding data randomly. On the subset of data that I do process, I explore using
+computation routines of differing fidelities to sample the data. Combining both of these
+techniques allows the cluster to avoid performing work.
 
@@
 by spinning workers up and down as necessary, and ensure results are as fresh as possible.
+
+The goal of Sr is to be a MapReduce-style framework for processing streams. Such a
+framework should include the ability to kill or discard tasks and provide serveral
+different computation routines for workers to choose among.
 
@@
 communicate with the master. The master and other nodes communicate with each other by issuing
-HTTP requests to a simple server on each node. I decided to make use of a library [Sinatra.rb]
+HTTP requests to a simple server on each node. I decided to make use of a library~\cite{sinatrarb}
 providing the server functionality because there was a low barrier to getting inter-node
@@
 Sr sends the source of the Jobfile to every node participating in the job and uses eval to
-obtain a local instance of the Jobfile class. An example jobfile can be found at [github].
+obtain a local instance of the Jobfile class. An example jobfile can be found at~\cite{github}.
 
@@
 1 collector, and 1 master. Roles are partitioned among nodes as shown in
-Figure~\ref{fig:clusterDiagram}. Worker nodes were XVM [SIPB] VMs provisioned with 128MB RAM each.
+Figure~\ref{fig:clusterDiagram}. Worker nodes were XVM~\cite{sipb:xvm} VMs provisioned with 128MB RAM each.
 The master, spout, fetcher, and collector ran on my laptop, a mid-2010 Macbook Air with 4GB of RAM.
@@
 To run the job, I had to create a spout and find a source of data. For data, I acquired a
-Wikipedia dump of the Featured Articles category. I used Wikipedia’s xml exporter
-[Special:export] on January 9, 2012.
+Wikipedia dump of the Featured Articles category. I used Wikipedia’s xml
+exporter~\cite{wikipedia:pecial:export} on January 9, 2012.
 
 To serve the data, I munged it into a YAML file containing a hash of
-\lstinline[language=Ruby]{article_id : fulltext}. To store fulltext, I base64 encoded it and
+\begin{center}
+$\texttt{article\_id}\rightarrow\texttt{fulltext}$.
+\end{center}
+To store fulltext, I base64 encoded it and
 deflated it using zlib. This requires workers to inflate and decode the fulltext before they

### 2012-05-04 paper/paper.tex
Add conclusion

@@
 
+\section{Conclusion}
+I have extended the ideas of approximate computations to a MapReduce-style framework and shown
+that it is feasible to tune the input parameters of a job to achieve sufficient precision and
+recall for a particular application.
+
+I have taken a different approach to streaming MapReduce by treating data not as a batch, but
+as a stream. At any given point in the execution of a job, the collectors will have accurate
+(so far as the job parameters allow) results for data seen until that point. This approach
+guarantees freshness and makes it easier to incorporate new data into an existing computation,
+yet it suffers from being limited to online aggregations.
+
+The Sr source code is open source and available at:
+\begin{center}
+  \url{https://github.com/lopopolo/sr}
+\end{center}
+
 \bibliography{paper}{}

### 2012-05-05 paper/paper.tex
Fix citation
Editing pass

@@
 every entry to uncover trends, especially when one only cares about the most prominent
-trends or results. Google runs PageRank on the entire Internet, but if
-it only did on half of the pages it crawls, it would likely still have a usable
-index for delivering the first 5 pages of results.
+trends or results. This type of workflow lends itself naturally to top-k-style computations,
+data sampling tasks, and other cases where perfect-fidelity results are not required.
+%Google runs PageRank on the entire Internet, but if
+%it only did on half of the pages it crawls, it would likely still have a usable
+%index for delivering the first 5 pages of results.
 
@@
 try to uncover through analysis. In this paper, I explore the possibility of
-discarding data randomly. On the subset of data that I do process, I explore using
+discarding data randomly while trying to maintain a target accuracy level.
+On the subset of data that I do process, I explore using
 computation routines of differing fidelities to sample the data. Combining both of these
@@
 
-One of the problems with MapReduce that Google has solved with Caffeine is how to
+One of the problems with MapReduce is how to
 incorporate new data into an already analyzed task. MapReduce simply says to rerun
@@
 A simpler way to incorporate new data is to treat data not as a constant, but as a
-stream. By processing data on demand, one avoids repeating work, can save resources
-by spinning workers up and down as necessary, and ensure results are as fresh as possible.
+stream. By processing data on demand, one avoids repeating work involved in reprocessing
+data, can save resources
+by spinning workers up and down as necessary, and ensure results are as fresh as possible
+by incorporating data into the result as soon as it arrives.
 
-The goal of Sr is to be a MapReduce-style framework for processing streams. Such a
-framework should include the ability to kill or discard tasks and provide serveral
-different computation routines for workers to choose among.
+The goal of Sr is to provide a MapReduce-style framework for processing streams. Such a
+framework should include the ability to kill or discard tasks and be capable of
+providing workers with serveral different computation routines to choose among.
 
@@
 Sr is a distributed system for processing streams that can choose to kill tasks or
-limit the amount of work it performs per task. Its design is modular; there are five
-different types of nodes in an Sr cluster (spout, fetcher, worker, collector, master).
+limit the amount of work it performs per task. Its design is modular and there are five
+different types of nodes in an Sr cluster: spout, fetcher, worker, collector, master.
 \subsection{Spout}
-Spouts are network-connected machines that generate data for the Sr cluster to process.
+Spouts are network-connected machines that generate data for an Sr cluster to process.
 Examples include a machine that tails a log file or an API like the Twitter tweet
@@
 in the MapReduce framework. Each worker receives a fraction of the total input data
-and each worker’s tasks are independent of other workers’.
+and each worker's tasks are independent of other workers'.
 
 Workers are responsible for fulfilling the main design goals of Sr. Workers may choose
-to kill a task preemptively or if it does not complete before a timeout. Additionally,
+to kill a task preemptively or greedily if it does not complete before a timeout. Additionally,
 workers may choose among a variety of routines for performing computation on a datum.
@@
 such that its estimated fraction of work is above a configured threshold.
+The total work estimator is used as a proxy for accuracy when a worker updates
+this metric. This metric also takes into account the number of tasks it has killed
+for any reason.
 
-Because one of Sr’s goals is to process (potentially infinite) streams, workers do not
+Because one of Sr's goals is to process (potentially infinite) streams, workers do not
 save their progress to disk and are forgetful; once the master queries a worker for its
@@
 continues processing. As a consequence, workers are easy to add or remove from the worker
-pool because they don’t need to be initialized with long-term job state. Additionally, as
+pool because they don't need to be initialized with long-term job state. Additionally, as
 long as the master polls workers frequently enough, when a worker fails, only a small
@@
 \subsection{Collector}
-Collector nodes aggregate the results of all workers. Each collector acts as a reducer
+Collector nodes aggregate the results of all workers. Each collector acts as a reducer would
 in the MapReduce framework if MapReduce used a single reducer for all of the mappers.
@@
 is produced from workers as opposed to after all mappers have completed. This limits the
-type of aggregation collectors can do to online operations.
+types of stateless aggregation collectors can do to online operations. (Of course, a collector
+can choose to retain copies of individual worker results and re-reduce them each time more
+results are receieved, but this is not in the spirit of the framework.)
 
@@
 
-Sr accomplishes this configuration with a Jobfile. Jobfiles are instances of a special class
+Sr achieves this configuration with a Jobfile. Jobfiles are instances of a special class
 provided by the Sr framework. This class exposes several methods that can be invoked by a
@@
 
-The use of eval to instantiate Jobfile objects and the implementation language’s (Ruby)
+The use of eval to instantiate Jobfile objects and the implementation language's (Ruby)
 ability to monkeypatch classes means that jobs can be modified on the fly just by sending
 an updated Jobfile to job participants. For example, a job can be made lower fidelity in
-the face of an impending time constraint or higher fidelity if more workers are added to
-the cluster.
+the face of an impending time constraint, higher fidelity if more workers are added to
+the cluster, or gracefully killing fetchers which allows the job to end after all of the
+various job queues are empty.
 \subsection{Fault Tolerance}
@@
 Fetchers can fail. The only consequence of fetcher failure is that some of the input stream is
-lost forever. Since streams contain much data and are likely stored permanently elsewhere on disk
+lost forever. Since streams contain much data and are possibly stored permanently elsewhere on disk
 Sr does not attempt to recover this data.
@@
 progress mitigates the consequences of worker failure. For jobs that run for minutes or hours,
-100ms of lost work is << 0.1\% of the total. Sr can simply treat these lost tasks as preemptively
+100ms of lost work is $\ll0.1\%$ of the total. Sr can simply treat these lost tasks as preemptively
 killed, which is already expected by the cluster.
@@
 Each collector is an exact replica of all others. Collector failure does not impact correctness of
-the results delivered by any other collector.
+the results delivered by any other collector. If no collectors are online, the data meant for them
+sits in a queue on the master. Bringing another collector online will allow these and future results
+to be aggregated.
 \subsection{Killing Tasks and Working Less}
@@
 \label{sec:methodology}
-The cluster I used to test Sr is a 5-node network consisting of 1 spout, 1 fetcher, 4 workers,
-1 collector, and 1 master. Roles are partitioned among nodes as shown in
-Figure~\ref{fig:clusterDiagram}. Worker nodes were XVM~\cite{sipb:xvm} VMs provisioned with 128MB RAM each.
-The master, spout, fetcher, and collector ran on my laptop, a mid-2010 Macbook Air with 4GB of RAM.
+The cluster I used to test Sr is a 5-node network consisting of~1 spout,~1 fetcher,~4 workers,~1
+collector, and~1 master. Roles were partitioned among nodes as shown in
+Figure~\ref{fig:clusterDiagram}. Worker nodes were XVM~\cite{sipb:xvm} VMs provisioned with~128MB RAM each.
+The master, spout, fetcher, and collector ran on a mid-2010 Macbook Air laptop with~4GB of RAM.
 
@@
 The job I ran was a word counter. The collector emits a hash whose keys are words and whose
-values are the frequency that word has occurred in the test corpus.
+values are the frequency the key occurred in the test corpus.
 
 To run the job, I had to create a spout and find a source of data. For data, I acquired a
-Wikipedia dump of the Featured Articles category. I used Wikipedia’s xml
-exporter~\cite{wikipedia:pecial:export} on January 9, 2012.
+Wikipedia dump of the Featured Articles category. I used Wikipedia's xml
+exporter~\cite{wikipedia:special:export} on January~9,~2012.
 
@@
 
-Workers are initialized with the 3 computation routines shown in Table~\ref{table:workerTasks}.
+Workers are initialized with the~3 computation routines shown in Table~\ref{table:workerTasks}.
 
@@
 \end{tabularx}
-\caption{Computation routines used by Sr workers}
+\caption{Computation routines used by Sr workers.}
 \label{table:workerTasks}
@@
 
-The results of the word count job are then used in a script to compute the top 100 words.
+The results of the word count job were then used in a script to compute the top~100 words.
 The cluster and word count job could be used in a two-stage top-k job. This script filters
@@
 
-The distribution shown in Figure~\ref{fig:wordDist} is long-tailed, meaning that killing
+The distribution shown in Figure~\ref{fig:wordDist} is long-tailed. This implies that killing
 tasks will impact the tail of the distribution more than the head.
@@
 Task killing should least impact the head of the word distribution.
-Figure~\ref{fig:precision} shows that even with a kill rate of 0.8 and a work level of
-0.4, meaning that the cluster only looks at 8\% of the words in the corpus, the results
-are at least 80\% accurate. Increasing the work level, which increases the fidelity of
-results emitted by workers, also increases the fidelity of the top 100 results.
+Figure~\ref{fig:precision} shows that even with a kill rate of~0.8 and a work level of~0.4,
+meaning that the cluster only looks at 8\% of the words in the corpus, the results
+are at least~80\% accurate. Increasing the work level, which increases the fidelity of
+results emitted by workers, also increases the fidelity of the top~100 results.
 
@@
 \includegraphics[width=\linewidth]{top-100-precision.png}
-\caption{Number of top 100 results returned in the top-100 by the word count job.}
+\caption{Fraction of the top~100 results returned in the top-100 by the word count job.}
 \label{fig:precision}
@@
 accuracy of the top-100 classifier, is always higher than the fraction of the input
-examined (kill rate * work level). Setting the work level to 0.4 nets a greater increase
-in job accuracy versus fraction of words examined, with accuracy approximately 1.75 times
+examined (kill rate * work level). Setting the work level to~0.4 nets a greater increase
+in job accuracy versus fraction of words examined, with accuracy approximately~1.75 times
 more than the fraction of words examined.
@@
 Table~\ref{table:runtime} shows the effect of varying the kill rate and work level. The row
-with kill~rate~=~0.0 and work~level~=~1.0 represents the perfect, MapReduce-style, execution
+with kill~rate~$=0.0$ and work~level~$=1.0$ represents the perfect, MapReduce-style, execution
 of the word count job. The only consistent reduction in execution time is a result of
@@
 \begin{table}
-\begin{tabularx}{\linewidth}{|X|X|X|}
+\begin{tabularx}{\linewidth}{|c|c|X|}
 \hline
@@
 
-Notably, simply by killing tasks, Sr is able to achieve over a 5 times speedup compared
-to the perfect execution while still returning about 84 of the top-100 words.
+Notably, simply by killing tasks, Sr is able to achieve over a~5 times speedup compared
+to the perfect execution while still returning about~84 of the top~100 words.
 
@@
 In Section~\ref{sec:master} I mentioned design difficulties relating to the master and using HTTP
-servers for sending messages between nodes. I initially chose to use HTTP requests with POST payloads
+requests for sending messages between nodes. I initially chose to use HTTP requests with POST payloads
 to send data and results between nodes because of its low barrier to entry; however, initiating many
@@
 
-In order to mitigate the effects of this problem, I batched individual requests into groups of 5. This
+In order to mitigate the effects of this problem, I batched individual requests into groups of~5. This
 lowered the number of connections I was initiating but it also limited the parallelism of the cluster
@@
 it and all active nodes. Communication channels should be established when nodes come online.
-Possible solutions include writing to a socket or using a higher abstraction like AMPQ. AMPQ
-is appealing because it relieves the master from handling queues.
+Possible solutions include writing to a socket or using a higher abstraction like AMPQ\@.
+AMPQ is appealing because it also relieves the master from handling queues.
 

### 2012-05-05 paper/paper.tex
Properly set the document as two column
Start related work section

@@
-\documentclass[12pt]{article}
+\documentclass[12pt,twocolumn]{article}
 
@@
 \begin{document}
-\twocolumn
 \maketitle
@@
 the growing amount of data in the world. Now with the open source Apache Hadoop
-and Pig~\cite{piglatin}, it is easy to process and query the terabytes of data an organization
+and Pig~\cite{Olston:2008:PLN:1376616.1376726}, it is easy to process and query
+the terabytes of data an organization
 may collect. With terabytes of data, however, it is scarcely necessary to examine
@@
 \label{sec:relwork}
+% data stream management system
+% continuous queries
+%   sr doesn't do this, instead it operates on snapshots
+%   this is how online mapreduce works
+% append only data sets == Chronicle data model
+%   views maintained incrementally without storing any chronicles (data items)
+% sequencing of streams and sliding windows
+%   sr doesn't do this
+% Aurora - load shedding based on app specific QoS
+% approximate answers
+%   baked in to Sr
+%
+
+Sr builds of previous work in the areas of MapReduce and Data Stream Management Systems.
+
+\subsection{MapReduce}
+There is a rich research field around MapReduce. This section details work related to adapting
+MapReduce to a streaming environment.
+
+The Hadoop Online Prototype~\cite{Condie:EECS-2009-136} adds streaming to the MapReduce framework
+by removing the materialize phase between mappers and reducers and between phases of a
+MapReduce pipeline. Results are streamed from mappers to reducers as they become available.
+At any given point, each reducer maintains an in-progress snapshot of the MapReduce job's
+progress up to that point. This removes the synchronization barriers inherient in MapReduce
+and allows incremental progress to be observed.
+
+This approach is in contrast to the continuous query approach taken by many other streaming
+systems.
+
+\subsection{Data Stream Management Systems}
+In their overview on data stream projects~\cite{Babcock:2002:MID:543613.543615},
+a new class of data streaming applications
+called \emph{Data Stream Management Systems} (\emph{DSMSes}) are discussed. Sr is a type of DSMS that
+includes some properties found in other systems.
+
+The \emph{Chronicle Data Model}~\cite{Jagadish:1995:VMI:212433.220201} describes an
+append-only stream of tuples. Such
+streams lend themselves to incremental reads and incremental processing. In addition to incremental
+updates, the Chronicle Data Model also seeks to update results incrementally without storing the
+data itself.
+
+The Aurora system~\cite{Carney:2002:MSN:1287369.1287389} introduces the concept of
+\emph{load shedding}, or compensating for
+resource overload by comparing job specific quality of service metrics with target levels.
 

### 2012-05-05 paper/paper.tex
Add section about data stream model

@@
 data itself.
+
+The \emph{Data Stream Model}~\cite{Babcock:2002:MID:543613.543615} is a refinement of the Chronicle
+Data Model. It has the following properties: stream items may arrive out of order,
+streams are potentially unbounded in size, elements in the stream are discared after they are
+processed. This is the data model that Sr uses.
 
@@
 \end{verbatim}
-\caption{Topology of the test Sr cluster used in the word count case study. Each box is a single machine.}
+\caption{Topology of the test Sr cluster used in the word count case study. Each box represents a single machine.}
 \label{fig:clusterDiagram}

### 2012-05-05 paper/paper.tex
StreamReduce!

@@
 
-\title{Sr: Processing Data Streams and Avoiding Work}
+\title{StreamReduce: Processing Data Streams\\and Avoiding Work}
 \author{Ryan Lopopolo\\
+Massachusetts Institute of Technology\\
 \texttt{lopopolo@mit.edu}}
@@
 
-The goal of Sr is to provide a MapReduce-style framework for processing streams. Such a
+The goal of StreamReduce is to provide a MapReduce-style framework for processing streams. Such a
 framework should include the ability to kill or discard tasks and be capable of
@@
 an overview of related work on distributed stream processing as well as dynamic and
-approximate computations. Section~\ref{sec:design} details how I designed Sr.
+approximate computations. Section~\ref{sec:design} details how I designed StreamReduce.
 Section~\ref{sec:methodology} explains the methodology used to perform a cvase study
-using Sr. Section~\ref{sec:evaluation} evaluates the effectiveness of Sr in the case study.
-Section~\ref{sec:discussion} enumerates issues with Sr's current implementation.
+using StreamReduce. Section~\ref{sec:evaluation} evaluates the effectiveness of StreamReduce in the case study.
+Section~\ref{sec:discussion} enumerates issues with StreamReduce's current implementation.
 
@@
 % approximate answers
-%   baked in to Sr
+%   baked in to StreamReduce
 %
 
-Sr builds of previous work in the areas of MapReduce and Data Stream Management Systems.
+StreamReduce builds of previous work in the areas of MapReduce and Data Stream Management Systems.
 
@@
 a new class of data streaming applications
-called \emph{Data Stream Management Systems} (\emph{DSMSes}) are discussed. Sr is a type of DSMS that
+called \emph{Data Stream Management Systems} (\emph{DSMSes}) are discussed. StreamReduce is a type of DSMS that
 includes some properties found in other systems.
@@
 streams are potentially unbounded in size, elements in the stream are discared after they are
-processed. This is the data model that Sr uses.
+processed. This is the data model that StreamReduce uses.
 
@@
 \label{sec:design}
-Sr is a distributed system for processing streams that can choose to kill tasks or
+StreamReduce is a distributed system for processing streams that can choose to kill tasks or
 limit the amount of work it performs per task. Its design is modular and there are five
-different types of nodes in an Sr cluster: spout, fetcher, worker, collector, master.
+different types of nodes in an StreamReduce cluster: spout, fetcher, worker, collector, master.
 \subsection{Spout}
-Spouts are network-connected machines that generate data for an Sr cluster to process.
+Spouts are network-connected machines that generate data for an StreamReduce cluster to process.
 Examples include a machine that tails a log file or an API like the Twitter tweet
@@
 
-Workers are responsible for fulfilling the main design goals of Sr. Workers may choose
+Workers are responsible for fulfilling the main design goals of StreamReduce. Workers may choose
 to kill a task preemptively or greedily if it does not complete before a timeout. Additionally,
@@
 
-Because one of Sr's goals is to process (potentially infinite) streams, workers do not
+Because one of StreamReduce's goals is to process (potentially infinite) streams, workers do not
 save their progress to disk and are forgetful; once the master queries a worker for its
@@
 Collectors also expose an API endpoint for accessing the results of a job. This endpoint
-can be used by another spout to chain Sr jobs together.
+can be used by another spout to chain StreamReduce jobs together.
 \subsection{Master}
 \label{sec:master}
-There is one master node per Sr network. It has a function similar to the jobtracker in
+There is one master node per StreamReduce network. It has a function similar to the jobtracker in
 MapReduce. New jobs are scheduled with the master and it initializes other nodes in the
@@
 
-Sr achieves this configuration with a Jobfile. Jobfiles are instances of a special class
-provided by the Sr framework. This class exposes several methods that can be invoked by a
+StreamReduce achieves this configuration with a Jobfile. Jobfiles are instances of a special class
+provided by the StreamReduce framework. This class exposes several methods that can be invoked by a
 given node to provide configuration parameters or execute code on its behalf. Most of the
-routines that advance the progress of an Sr job are wrappers around these Jobfile methods.
+routines that advance the progress of an StreamReduce job are wrappers around these Jobfile methods.
 
-Sr sends the source of the Jobfile to every node participating in the job and uses eval to
+StreamReduce sends the source of the Jobfile to every node participating in the job and uses eval to
 obtain a local instance of the Jobfile class. An example jobfile can be found at~\cite{github}.
@@
 \subsection{Fault Tolerance}
-Sr can sustain the failure of any node other than the master. Because the master is responsible
+StreamReduce can sustain the failure of any node other than the master. Because the master is responsible
 for shuffling data between fetchers, workers, and collectors, a job cannot make progress without
@@
 lost forever. Since streams contain much data and are possibly stored permanently elsewhere on disk
-Sr does not attempt to recover this data.
+StreamReduce does not attempt to recover this data.
 
@@
 progress mitigates the consequences of worker failure. For jobs that run for minutes or hours,
-100ms of lost work is $\ll0.1\%$ of the total. Sr can simply treat these lost tasks as preemptively
+100ms of lost work is $\ll0.1\%$ of the total. StreamReduce can simply treat these lost tasks as preemptively
 killed, which is already expected by the cluster.
@@
 \subsection{Killing Tasks and Working Less}
-A design goal of Sr is to compute meaningful results from a stream and to do so while not
-processing every datum one-to-one. Sr achieves this goal in two different ways. First, workers
+A design goal of StreamReduce is to compute meaningful results from a stream and to do so while not
+processing every datum one-to-one. StreamReduce achieves this goal in two different ways. First, workers
 may kill tasks preemptively to avoid the time and resource costs associated with processing
@@
 \label{sec:methodology}
-The cluster I used to test Sr is a 5-node network consisting of~1 spout,~1 fetcher,~4 workers,~1
+The cluster I used to test StreamReduce is a 5-node network consisting of~1 spout,~1 fetcher,~4 workers,~1
 collector, and~1 master. Roles were partitioned among nodes as shown in
@@
 \end{verbatim}
-\caption{Topology of the test Sr cluster used in the word count case study. Each box represents a single machine.}
+\caption{Topology of the test StreamReduce cluster used in the word count case study. Each box represents a single machine.}
 \label{fig:clusterDiagram}
@@
 \end{tabularx}
-\caption{Computation routines used by Sr workers.}
+\caption{Computation routines used by StreamReduce workers.}
 \label{table:workerTasks}
@@
 \label{sec:evaluation}
-To evaluate Sr, I explore the precision and recall of the word count test job as well as the
+To evaluate StreamReduce, I explore the precision and recall of the word count test job as well as the
 speedup factor associated with varying the kill rate and target work level.
@@
 \subsubsection{Word Count Job Accuracy}
-Because I am running a top-k job, I compute the $F_{0.5}$-score of the Sr results as
+Because I am running a top-k job, I compute the $F_{0.5}$-score of the StreamReduce results as
 opposed to the $F1$-score because I care more about precision of the top k than recall
@@
 \subsection{Speedup}
-Sr is able to achieve a speedup over a MapReduce-style computation through three mechanisms:
+StreamReduce is able to achieve a speedup over a MapReduce-style computation through three mechanisms:
 providing multiple computation routines for the workers to choose from; varying the task kill
@@
 
-Notably, simply by killing tasks, Sr is able to achieve over a~5 times speedup compared
+Notably, simply by killing tasks, StreamReduce is able to achieve over a~5 times speedup compared
 to the perfect execution while still returning about~84 of the top~100 words.
@@
 \label{sec:discussion}
-This section describes deficiencies in the implementation of Sr used to run the case study
+This section describes deficiencies in the implementation of StreamReduce used to run the case study
 in this paper and goals for the next version of the system.
@@
 The mechanism for altering execution of a job as it is running described in Section~\ref{sec:jobfile}
-is not yet implemented. Adding this feature to Sr is a matter of adding an API endpoint
+is not yet implemented. Adding this feature to StreamReduce is a matter of adding an API endpoint
 to the servers run by each role and adding a bin-script to submit the new Jobfile.
@@
 
-The Sr source code is open source and available at:
+The StreamReduce source code is open source and available at:
 \begin{center}

### 2012-05-05 paper/paper.tex
Add acknowledgements section

@@
 
+\subsection*{Acknowledgments}
+I would like to acknowledge Martin Rinard for giving me direction for my initial idea
+and guiding me to apply the data stream model to StreamReduce; Sasa Misailovic for being
+a sounding board for ideas and providing me with background research; Daniel Erenrich for
+providing information about data stream management systems; and SIPB for providing the
+XVM service, which made deploying a StreamReduce cluster painless.
+
 \bibliography{paper}{}

### 2012-05-07 paper/paper.tex
another editing pass

@@
 the job with the new data included. Others have solved this problem by batching data
-into chunks and continuously spawning MapReduce jobs to incorporate the new data.
+into chunks and continuously spawning MapReduce jobs to incorporate the new data
+and incrementally storing updates in an external database instead of relying on
+the file system for enforcing the synchronization barrier.
 
@@
 data, can save resources
-by spinning workers up and down as necessary, and ensure results are as fresh as possible
+by spinning workers up and down as necessary, and ensures results are as fresh as possible
 by incorporating data into the result as soon as it arrives.
@@
 approximate computations. Section~\ref{sec:design} details how I designed StreamReduce.
-Section~\ref{sec:methodology} explains the methodology used to perform a cvase study
+Section~\ref{sec:methodology} explains the methodology used to perform a case study
 using StreamReduce. Section~\ref{sec:evaluation} evaluates the effectiveness of StreamReduce in the case study.
@@
 a new class of data streaming applications
-called \emph{Data Stream Management Systems} (\emph{DSMSes}) are discussed. StreamReduce is a type of DSMS that
-includes some properties found in other systems.
+called \emph{Data Stream Management Systems} (\emph{DSMS}es) is discussed.
+StreamReduce is a type of DSMS that includes some properties found in other systems.
 
@@
 resource overload by comparing job specific quality of service metrics with target levels.
+StreamReduce aims to incorporate load shedding to dynamically tune jobs in the face of
+impending time and resource constraints.
 

### 2012-05-07 paper/paper.tex
Dynamic knobs related work

@@
 
-StreamReduce builds of previous work in the areas of MapReduce and Data Stream Management Systems.
+StreamReduce builds of previous work in the areas of MapReduce, Data Stream Management Systems,
+and approximation algorithms.
 
@@
 impending time and resource constraints.
+
+\subsection{Approximation Algorithms}
+An alternative to load shedding to cope with high stream throughput is to perform approximate
+computations on stream data.
+
+Dynamic Knobs~\cite{Hoffmann:2011:DKR:1950365.1950390} describes a mechanism to explore the
+accuracy-performance tradeoff space to adjust dynamically adjust program tuning parameters
+to changes in the execution environment. This allows programs to do things such as
+utilize more resources if they become available, use less power if power rates spike,
+or use less accurate computations in the face of an impending time constraint.
+
+The most important piece Dyanmic Knobs offers to the DSMS space is dynamic
+\emph{peak load provisioning}. Their system can adjust downward the amount of resources,
+machines, etc. required for normal load and quickly adjust these levels back up to
+handle load spikes. Combined with Aurora's load shedding, peak load provisioning can
+be used to create a DSMS that uses less resources in both the normal and peak load
+states.
 

### 2012-05-07 paper/paper.tex
POPL paper

@@
 states.
+
+Accuracy-aware transformations~\cite{Zhu:2012:RAP:2103656.2103710} are a class of transformations
+that alter a computation according to a set of probabilstic weights and an accuracy
+target such that the computation performs more efficiently. StreamReduce uses the subclass
+of transformations called \emph{substitution transformations} in worker nodes to adjust
+the runtime characteristics of per-datum computation.
 

### 2012-05-07 paper/paper.tex
More edits

@@
 an overview of related work on distributed stream processing as well as dynamic and
-approximate computations. Section~\ref{sec:design} details how I designed StreamReduce.
+approximate computations. Section~\ref{sec:design} details the design of StreamReduce.
 Section~\ref{sec:methodology} explains the methodology used to perform a case study
@@
 
+Aurora also introduces the operators \texttt{filter}, \texttt{map}, and \texttt{union} for
+manipulating streams. StreamReduce implements these operators at the worker and fetcher nodes.
+
 \subsection{Approximation Algorithms}
@@
 limit the amount of work it performs per task. Its design is modular and there are five
-different types of nodes in an StreamReduce cluster: spout, fetcher, worker, collector, master.
+different types of nodes in a StreamReduce cluster: spout, fetcher, worker, collector, master.
 \subsection{Spout}
-Spouts are network-connected machines that generate data for an StreamReduce cluster to process.
+Spouts are network-connected machines that generate data for a StreamReduce cluster to process.
 Examples include a machine that tails a log file or an API like the Twitter tweet
@@
 Fetchers are responsible for communicating with spouts and returning data for the
-workers to process. Fetchers may run indefinitely or return a status code indicating
+workers to process. This level of indirection allows for a variety of different
+configurations: A spout can emit data at such a high rate that using multiple fetchers
+returns more data to the cluster, multiple fetchers can each talk to a different spout,
+for example tailing logs from multiple machines, or fetchers can be set up redundantly
+to ensure that every datum emitted by a spout is processed.
+
+Fetchers may run indefinitely or return a status code indicating
 the fetching task is over.
@@
 Workers are responsible for fulfilling the main design goals of StreamReduce. Workers may choose
-to kill a task preemptively or greedily if it does not complete before a timeout. Additionally,
+to kill a task preemptively or, if it does not complete before a timeout, greedily. Additionally,
 workers may choose among a variety of routines for performing computation on a datum.
 Routines are ranked on a [0,1] scale based on the estimated fraction of total work it
-requires.
+requires. This rank is a proxy for the accuracy of a routine.
 
@@
 pool because they don't need to be initialized with long-term job state. Additionally, as
-long as the master polls workers frequently enough, when a worker fails, only a small
-fraction of the total work is lost. The master queries workers every 100ms by default.
+long as the master polls workers frequently enough, only a small
+fraction of the total work is lost upon worker failure.
+The master queries workers every 100ms by default.
 \subsection{Collector}
@@
 Collectors differ from MapReduce reducers in that they receive their data piecewise, as it
-is produced from workers as opposed to after all mappers have completed. This limits the
+is produced from workers, as opposed to after all mappers have completed. This limits the
 types of stateless aggregation collectors can do to online operations. (Of course, a collector
@@
 given node to provide configuration parameters or execute code on its behalf. Most of the
-routines that advance the progress of an StreamReduce job are wrappers around these Jobfile methods.
+routines that advance the progress of a StreamReduce job are wrappers around these Jobfile methods.
 
@@
 
-The use of eval to instantiate Jobfile objects and the implementation language's (Ruby)
+The use of eval to instantiate Jobfile objects and the implementation language's (ruby)
 ability to monkeypatch classes means that jobs can be modified on the fly just by sending
 an updated Jobfile to job participants. For example, a job can be made lower fidelity in
-the face of an impending time constraint, higher fidelity if more workers are added to
-the cluster, or gracefully killing fetchers which allows the job to end after all of the
+the face of an impending time constraint, be made higher fidelity if more workers are added to
+the cluster, or gracefully kill all fetchers which allows the job to end after all of the
 various job queues are empty.
@@
 Fetchers can fail. The only consequence of fetcher failure is that some of the input stream is
-lost forever. Since streams contain much data and are possibly stored permanently elsewhere on disk
-StreamReduce does not attempt to recover this data.
+lost forever. Because StreamReduce uses the Data Stream Model, it does not attempt to recover this data.
 
@@
 routines and the weights assigned to them must be adapted to fit the distribution of the data
-before the job starts (or updated in situ via a new Jobfile).
+before the job starts (or updated \emph{in situ} via a new Jobfile).
 
@@
 To evaluate StreamReduce, I explore the precision and recall of the word count test job as well as the
-speedup factor associated with varying the kill rate and target work level.
+speedup factor associated with varying the task kill rate and target work level.
 
@@
 Task killing should least impact the head of the word distribution.
-Figure~\ref{fig:precision} shows that even with a kill rate of~0.8 and a work level of~0.4,
+Figure~\ref{fig:precision} shows that even with a task kill rate of~0.8 and a work level of~0.4,
 meaning that the cluster only looks at 8\% of the words in the corpus, the results
@@
 \includegraphics[width=\linewidth]{top-100-precision.png}
-\caption{Fraction of the top~100 results returned in the top-100 by the word count job.}
+\caption{Fraction of the top~100 results returned in the top~100 by the word count job.}
 \label{fig:precision}
@@
 accuracy of the top-100 classifier, is always higher than the fraction of the input
-examined (kill rate * work level). Setting the work level to~0.4 nets a greater increase
+examined (task kill rate * work level). Setting the work level to~0.4 nets a greater increase
 in job accuracy versus fraction of words examined, with accuracy approximately~1.75 times
-more than the fraction of words examined.
+higher than the fraction of words examined.
 
@@
 
-Table~\ref{table:runtime} shows the effect of varying the kill rate and work level. The row
+Table~\ref{table:runtime} shows the effect of varying the task kill rate and work level. The row
 with kill~rate~$=0.0$ and work~level~$=1.0$ represents the perfect, MapReduce-style, execution
 of the word count job. The only consistent reduction in execution time is a result of
-increasing the kill rate. Increasing the kill rate exhibits a linear reduction in execution
+increasing the task kill rate. Increasing the task kill rate exhibits a linear reduction in execution
 time as the fraction of processed data linearly decreases.
@@
 \hline
-Kill rate & Work level & Average execution time [minutes] \\ \hline
+Task kill rate & Work level & Average execution time [minutes] \\ \hline
 0.0 & 1.0 & 11:35.5 \\ \hline
@@
 \end{tabularx}
-\caption{Impact of kill rate and work level on job execution time.}
+\caption{Impact of task kill rate and work level on job execution time.}
 \label{table:runtime}

### 2012-05-10 paper/paper.tex
clarify aurora operators
Rework introduction

@@
 \usepackage{url}
+\usepackage{hyperref}
 
@@
 Massachusetts Institute of Technology\\
-\texttt{lopopolo@mit.edu}}
+\href{mailto:lopopolo@mit.edu}{\texttt{lopopolo@mit.edu}}}
 
@@
 One of the fundamental problems MapReduce was created to solve was processing
-the growing amount of data in the world. Now with the open source Apache Hadoop
+the growing amount of data in the world.
+MapReduce lends itself naturally to top-k-style computations,
+data sampling tasks, and other cases where perfect-fidelity results are not required.
+Now with the open source Apache Hadoop
 and Pig~\cite{Olston:2008:PLN:1376616.1376726}, it is easy to process and query
-the terabytes of data an organization
-may collect. With terabytes of data, however, it is scarcely necessary to examine
+the terabytes of data an organization may collect.
+%The widespread use of these tools to solve problems they weren't designed for motivates
+%us to explore how we can save time, resources, and prevent faults in the execution of
+%such MapReduce tasks.
+
+With terabytes of data, however, it is scarcely necessary to examine
 every entry to uncover trends, especially when one only cares about the most prominent
-trends or results. This type of workflow lends itself naturally to top-k-style computations,
-data sampling tasks, and other cases where perfect-fidelity results are not required.
-%Google runs PageRank on the entire Internet, but if
-%it only did on half of the pages it crawls, it would likely still have a usable
-%index for delivering the first 5 pages of results.
+trends or results.
+How does one decide which data to process then? Ultimately, this is problem dependent;
+however, selctively deciding which data to
+log is problematic because it can systemically mask some of the trends one would
+try to uncover through analysis. In this paper, I introduce StreamReduce, a distributed system
+for processing data streams. With StreamReduce I explore:
+\begin{itemize}
+  \item
+    Randomly discarding data while trying to maintain a target accuracy level.
+  \item
+    Processing data using a variety of computation routines, some of which are less
+    accurate than others.
+\end{itemize}
+Combining both of these techniques allows the cluster to save time by executing faster,
+save resources by avoiding the need to process every datum, and minimize the impact of faults
+in the execution of a job by treating failed tasks as discarded tasks.
 
-How does one decide which data to process then? Selctively deciding which data to
-log is problematic because it can systemically mask some of the trends one would
-try to uncover through analysis. In this paper, I explore the possibility of
-discarding data randomly while trying to maintain a target accuracy level.
-On the subset of data that I do process, I explore using
-computation routines of differing fidelities to sample the data. Combining both of these
-techniques allows the cluster to avoid performing work.
-
-One of the problems with MapReduce is how to
-incorporate new data into an already analyzed task. MapReduce simply says to rerun
+Another limitation of MapReduce is batch processing. How does one
+incorporate new data into an already analyzed task? MapReduce simply says to rerun
 the job with the new data included. Others have solved this problem by batching data
@@
 The goal of StreamReduce is to provide a MapReduce-style framework for processing streams. Such a
-framework should include the ability to kill or discard tasks and be capable of
-providing workers with serveral different computation routines to choose among.
-
-The remainder of this paper is organized as follows. Section~\ref{sec:relwork} provides
-an overview of related work on distributed stream processing as well as dynamic and
-approximate computations. Section~\ref{sec:design} details the design of StreamReduce.
-Section~\ref{sec:methodology} explains the methodology used to perform a case study
-using StreamReduce. Section~\ref{sec:evaluation} evaluates the effectiveness of StreamReduce in the case study.
-Section~\ref{sec:discussion} enumerates issues with StreamReduce's current implementation.
+framework should include the ability to kill or discard tasks, be capable of
+providing workers with serveral different computation routines to choose among, and pass data
+between nodes using non-blocking routines.
 
@@
 
-Aurora also introduces the operators \texttt{filter}, \texttt{map}, and \texttt{union} for
+Aurora also introduces the non-blocking operators
+\texttt{filter}, \texttt{map}, and \texttt{union} for
 manipulating streams. StreamReduce implements these operators at the worker and fetcher nodes.

### 2012-05-10 paper/paper.tex
Add oopsla07 and ics06 to related work

@@
 This approach is in contrast to the continuous query approach taken by many other streaming
-systems.
+systems. StreamReduce uses this snapshot approach.
 
@@
 \emph{load shedding}, or compensating for
-resource overload by comparing job specific quality of service metrics with target levels.
+resource overload by comparing job specific quality of service metrics with target levels and
+dropping items from the data stream.
 StreamReduce aims to incorporate load shedding to dynamically tune jobs in the face of
-impending time and resource constraints.
+impending time and resource constraints. On the other hand, it may be the case that
+parts of a processing pipeline struggle to provide enough data to keep the next stage busy.
+In this case, a streaming system would like to implement
+\emph{early phase termination}~\cite{Rinard:2007:UEP:1297027.1297055}, or preemptively kill
+a stage in the pipeline that is not capable of keeping all workers busy.
 
@@
 
-The most important piece Dyanmic Knobs offers to the DSMS space is dynamic
+The most important piece Dynamic Knobs offers to the DSMS space is dynamic
 \emph{peak load provisioning}. Their system can adjust downward the amount of resources,
@@
 the runtime characteristics of per-datum computation.
+
+The combination of load shedding, task killing and substitution transformations presents
+an opportunity for the results of a computation performed by StreamReduce to be distorted.
+Rinard~\cite{Rinard:2006:PAB:1183401.1183447} describes a method for bounding the distortion
+introduced when discarding tasks. By breaking a computation into tasks, which in StreamReduce
+consist of processing an individual datum at a worker, we can measure a
+\emph{probabilistic distortion model} for a job, which gives bounds on its accuracy at different
+task failure rates. I use this approach in the case study discussed in Section~\ref{sec:evaluation}.
 

### 2012-05-10 paper/paper.tex
Rework section 3

@@
 limit the amount of work it performs per task. Its design is modular and there are five
-different types of nodes in a StreamReduce cluster: spout, fetcher, worker, collector, master.
+different types of nodes in a StreamReduce cluster:
+\begin{itemize}
+  \item
+    \textbf{Spout}: A node external to the cluster that is a source of streaming data.
+  \item
+    \textbf{Fetcher}: Communicates with spouts to provide data for workers.
+  \item
+    \textbf{Worker}: Processes data returned by fetchers. They are the source of parallel computation
+    in the cluster.
+  \item
+    \textbf{Collector}: Aggregates results from all workers and makes the result accessible via an API.
+  \item
+    \textbf{Master}: Manages the cluster by bringing nodes online to complete jobs. It is reponsible
+    for all internode communication and storing to-be-processed data in several queues.
+\end{itemize}
+Figure~\ref{fig:systemdiagram} shows a system diagram of StreamReduce.
+
+\begin{figure*}
+\includegraphics[width=\textwidth]{system-diagram.png}
+\caption{Overview of data flow in the execution of a StreamReduce job. Load shedding occurs at point A. Task killing occurs at point B.}
+\label{fig:systemdiagram}
+\end{figure*}
+
 \subsection{Spout}
@@
 collectors, respectively.
+
+\begin{figure}
+\includegraphics[width=\linewidth]{master-control-queue.png}
+\caption{The master communicates directly with all nodes to pass them control messages. Nodes respond directly to the master with their results.}
+\label{fig:mastercontrolqueue}
+\end{figure}
+
+Figure~\ref{fig:mastercontrolqueue} shows how control messages are passed from the master
+to all other nodes in the cluster. The master communicates directly to each node and nodes
+reply directly to the master when they have completed their task. With these control messages,
+the master advances the state of the job. Such messages include telling a fetcher to fetch data
+from a spout, giving data to a worker to process, and flushing results to collectors.
+
 \subsection{Configuring a Cluster for a Job}

### 2012-05-10 paper/paper.tex
Prettify cluster config image
Tweak methodology section

@@
 Figure~\ref{fig:clusterDiagram}. Worker nodes were XVM~\cite{sipb:xvm} VMs provisioned with~128MB RAM each.
-The master, spout, fetcher, and collector ran on a mid-2010 Macbook Air laptop with~4GB of RAM.
+The master, spout, fetcher, and collector ran on a mid-2010 Macbook Air laptop with~4GB of RAM. I configured
+the cluster to kill tasks on the master node, before they were shipped to workers.
 
 \begin{figure}
-\begin{verbatim}
-                  |--------|
-                - | worker |
-               /  |--------|
-|-----------| /   |--------|
-| master    | --- | worker |
-| spout     |     |--------|
-| fetcher   |     |--------|
-| collector | --- | worker |
-|-----------| \   |--------|
-               \  |--------|
-                - | worker |
-                  |--------|
-\end{verbatim}
-\caption{Topology of the test StreamReduce cluster used in the word count case study. Each box represents a single machine.}
+  \includegraphics[width=\linewidth]{sr-topology.png}
+  \caption{Topology of the test StreamReduce cluster used in the word count case study. Each square box represents a single machine. Each rounded box represents a StreamReduce role.}
 \label{fig:clusterDiagram}
@@
 
-To serve the data, I munged it into a YAML file containing a hash of
+To serve the data, I transformed it into a YAML file containing a hash of
 \begin{center}
@@
 out SEO stopwords~\cite{stopwords} to achieve more interesting results.
+
+I ran four trials of the word count job for every combination of work level and task kill
+rate I tested.
 

### 2012-05-10 test/stats.rb
Calculate f-score for new experiments

@@ -91,5 +91,26 @@ puts "%-5s%-10s%-10s%-10s%-10s%-10s%-10s%-10s%-10s" % ["exp", "t1 pre", "t1 reca
 end
 
 puts ""
+
+(15..18).each do |exp|
+  trial_results = ["#{exp}"]
+  (1...2).each do |run|
+    trial = {}
+    File.open(File.join(File.dirname(__FILE__), "datadumps", "experiment-#{exp}-run-#{run}.json")) do |f|
+      json = JSON.parse(f.read)
+      json.each_pair do |k,v|
+        trial[k.to_i] = v
+      end
+    end
+    top100s = getTopK(trial, 100)
+    top100g = getTopK(gold, 100)
+    trial_results << precision(top100g, top100s)
+    trial_results << recallForBottomK(gold, trial, 10000)
+  end
+  puts "%-5s%-10s%-10s" % trial_results
+end
+
+
+puts ""
 puts "%-25s%5d" % ["Precision (top k)", 100]
 puts "%-25s%5d" % ["Recall (bot k)", 10000]

### 2012-05-10 paper/paper.tex
Tweak Evaluation section

@@
 \includegraphics[width=\linewidth]{long-tail-ranks.png}
-\caption{The frequencies of words in the Wikipedia Featured Articles corpus have a long-tailed distribution.}
+\caption{The frequencies of words in the Wikipedia Featured Articles corpus have a long-tailed distribution. This graph has had stopwords~\cite{stopwords} filtered out of it.}
 \label{fig:wordDist}
@@
 
+\subsubsection{Recall}
+Recall in the tail of the distribution is most dependent on the work level of the word count job.
+Anything less than perfect computation of a datum leaves out words with a frequency of one.
+Figure~\ref{fig:recall} shows how recall improves as the work level increases. Task killing has
+the same effect on recall as using low fidelity computation routines, so recall decreases as
+the task kill rate does. Task killing dominates the impact of work level on recall as demonstrated
+by the two lines converging in Figure~\ref{fig:recall}.
+
+Poor recall statistics are acceptable because I am running a top-k job that focuses
+on good precision in the top~100. Because I use a weighted $F$-score, the poor recall's impact
+on measured accuracy is mitigated.
+
+\begin{figure}
+\includegraphics[width=\linewidth]{recall.png}
+\caption{Fraction of the bottom~10000 results returned in the result set by the word count job.}
+\label{fig:recall}
+\end{figure}
+
 \subsubsection{Word Count Job Accuracy}
@@
 
+The average reduction in $F_{0.5}$-score caused by reducing the work level form 0.8 to 0.4 is
+$0.231$ with a standard deviation of $0.025$. I performed four additional experiments with the
+work level set to $0.8$ and $0.4$ with the task kill rate set to $0.1$ and $0.7$. These experiments were
+not included in generating Figure~\ref{fig:fscore}. The average reduction in $F_{0.5}$-score between
+work level $0.8$ and $0.4$ in these experiments is $0.230$ with a standard deviation of
+$0.056$. These numbers show that a $0.4$ reduction in the work level leads to approximately a
+$0.23$ reduction in $F_{0.5}$-score.
+
 \subsection{Speedup}
@@
 \begin{table}
-\begin{tabularx}{\linewidth}{|c|c|X|}
+\begin{tabularx}{\linewidth}{|X|X|X|X|}
 \hline
-Task kill rate & Work level & Average execution time [minutes] \\ \hline
-0.0 & 1.0 & 11:35.5 \\ \hline
-0.0 & 0.4 & 10:33.8 \\ \hline
-0.0 & 0.8 & 10:30.8 \\ \hline
-0.2 & 0.4 & 08:25.8 \\ \hline
-0.2 & 0.8 & 08:37.8 \\ \hline
-0.4 & 0.4 & 06:54.0 \\ \hline
-0.4 & 0.8 & 06:28.2 \\ \hline
-0.6 & 0.4 & 04:14.7 \\ \hline
-0.6 & 0.8 & 04:13.7 \\ \hline
-0.8 & 0.4 & 02:33.3 \\ \hline
-0.8 & 0.8 & 02:15.0 \\ \hline
+Task kill rate & Work level & Average execution time [s] & $F_{0.5}$-score \\ \hline\hline
+0.0 & 1.0 & 696 & 1.000 \\ \hline
+0.0 & 0.8 & 631 & 0.939 \\ \hline
+0.0 & 0.4 & 634 & 0.725 \\ \hline\hline
+0.2 & 1.0 & 531 & 0.933 \\ \hline
+0.2 & 0.8 & 518 & 0.890 \\ \hline
+0.2 & 0.4 & 506 & 0.627 \\ \hline\hline
+0.4 & 1.0 & 393 & 0.829 \\ \hline
+0.4 & 0.8 & 388 & 0.797 \\ \hline
+0.4 & 0.4 & 414 & 0.552 \\ \hline\hline
+0.6 & 1.0 & 292 & 0.774 \\ \hline
+0.6 & 0.8 & 254 & 0.690 \\ \hline
+0.6 & 0.4 & 255 & 0.453 \\ \hline\hline
+0.8 & 1.0 & 144 & 0.541 \\ \hline
+0.8 & 0.8 & 135 & 0.489 \\ \hline
+0.8 & 0.4 & 153 & 0.290 \\ \hline
 \end{tabularx}
-\caption{Impact of task kill rate and work level on job execution time.}
+\caption{Impact of task kill rate and work level on job execution time and $F_{0.5}$-score.}
 \label{table:runtime}
@@
 to the perfect execution while still returning about~84 of the top~100 words.
+
+\subsection{Speed vs. Accuracy Tradeoffs}
+\begin{center}
+\begin{table*}
+  \begin{tabularx}{\linewidth}{|lr|lr|lr|}
+    \hline
+    \multicolumn{2}{|X|}{Work level = 1.0 and task kill rate = 0.0} &
+    \multicolumn{2}{|X|}{Work level = 0.8 and task kill rate = 0.4} &
+    \multicolumn{2}{|X|}{Work level = 0.4 and task kill rate = 0.8} \\ \hline
+    33225 & title & 21184 & title & 5982 & title \\ \hline
+    29356 & web & 18398 & web & 4689 & web \\ \hline
+    23095 & book & 13591 & journal & 4225 & journal \\ \hline
+    21821 & journal & 13429 & book & 3629 & year \\ \hline
+    20124 & year & 12770 & publisher & 3617 & publisher \\ \hline
+    19786 & publisher & 12550 & url & 3444 & url \\ \hline
+    19478 & url & 12220 & year & 3410 & book \\ \hline
+    17360 & news & 11511 & news & 3273 & news \\ \hline
+    16685 & accessdate & 11082 & united & 2968 & accessdate \\ \hline
+    16401 & united & 10691 & accessdate & 2582 & world \\ \hline
+  \end{tabularx}
+  \caption{Example top~10 results and their frequencies from several different job configurations. The top~10 do not change much one changes the paramters to make the job less accurate.}
+  \label{table:top10}
+\end{table*}
+\end{center}
+
+Because the word distribution is so skewed toward the head, there is a great potential to
+speed up the calculation by killing tasks without having to sacrifice too much accuracy.
+Additionally, Table~\ref{table:runtime} shows that the most significant time savings comes
+from increasing the kill rate and keeping the work level high yields about a~20 percentage point
+increase in $F_{0.5}$-score.
+
+The best combination of parameters is a high work level and as high a task kill rate one can
+manage with respect to one's target distortion level.
 

### 2012-05-10 test/stats.rb
More data extraction scripts

@@ -92,6 +92,26 @@ end
 
 puts ""
 
+(11..14).each do |exp|
+  trial_results = ["#{exp}"]
+  (1..4).each do |run|
+    trial = {}
+    File.open(File.join(File.dirname(__FILE__), "datadumps", "experiment-#{exp}-run-#{run}.json")) do |f|
+      json = JSON.parse(f.read)
+      json.each_pair do |k,v|
+        trial[k.to_i] = v
+      end
+    end
+    top100s = getTopK(trial, 100)
+    top100g = getTopK(gold, 100)
+    trial_results << precision(top100g, top100s)
+    trial_results << recallForBottomK(gold, trial, 10000)
+  end
+  puts "%-5s%-10s%-10s%-10s%-10s%-10s%-10s%-10s%-10s" % trial_results
+end
+
+puts ""
+
 (15..18).each do |exp|
   trial_results = ["#{exp}"]
   (1...2).each do |run|

### 2012-05-10 test/top10-exp.rb

@@ -1,0 +1,55 @@
+#!/usr/bin/env ruby
+
+$:.unshift "lib"
+require "sr/util"
+require "json"
+
+# get gold results
+gold = {}
+File.open(File.join(File.dirname(__FILE__), "gold.json")) do |f|
+  goldj = JSON.parse(f.read)
+  goldj.each_pair do |k,v|
+    gold[k.to_i] = v
+  end
+end
+
+# get stopwords
+require File.expand_path(File.join(File.dirname(__FILE__), "stopwords"))
+
+# remove the stopwords
+Stopwords.stopwords.each do |stopword|
+  gold.delete(stopword)
+end
+
+def getTopK(hash, k)
+  keys = hash.keys.sort.reverse[0, k]
+  n = 0
+  words = Hash.new(0)
+  keys.each do |freq|
+    hash[freq].each do |w|
+      words[w] = freq
+      n += 1
+      puts "#{freq} & #{w}"
+      break if n >= k
+    end
+    break if n >= k
+  end
+  words
+end
+
+getTopK(gold, 10)
+
+[5,10].each do |exp|
+  puts ""
+  (1...2).each do |run|
+    trial = {}
+    File.open(File.join(File.dirname(__FILE__), "datadumps", "experiment-#{exp}-run-#{run}.json")) do |f|
+      json = JSON.parse(f.read)
+      json.each_pair do |k,v|
+        trial[k.to_i] = v
+      end
+    end
+    getTopK(trial, 10)
+  end
+end
+

### 2012-05-10 paper/paper.tex
Editing pass. The end is near

@@
 \label{sec:intro}
-One of the fundamental problems MapReduce was created to solve was processing
+One of the fundamental problems MapReduce was created to solve is processing
 the growing amount of data in the world.
@@
 Data Model. It has the following properties: stream items may arrive out of order,
-streams are potentially unbounded in size, elements in the stream are discared after they are
+streams are potentially unbounded in size, and elements in the stream are discared after they are
 processed. This is the data model that StreamReduce uses.
@@
 Dynamic Knobs~\cite{Hoffmann:2011:DKR:1950365.1950390} describes a mechanism to explore the
-accuracy-performance tradeoff space to adjust dynamically adjust program tuning parameters
+accuracy-performance tradeoff space, dynamically adjusting program tuning parameters in response
 to changes in the execution environment. This allows programs to do things such as
@@
 \label{sec:master}
-There is one master node per StreamReduce network. It has a function similar to the jobtracker in
+There is one master node per StreamReduce cluster. It has a function similar to the jobtracker in
 MapReduce. New jobs are scheduled with the master and it initializes other nodes in the
@@
 
-StreamReduce sends the source of the Jobfile to every node participating in the job and uses eval to
+StreamReduce sends the source of the Jobfile to every node participating in the job and uses
+\texttt{eval} to
 obtain a local instance of the Jobfile class. An example jobfile can be found at~\cite{github}.
 
-The use of eval to instantiate Jobfile objects and the implementation language's (ruby)
+The use of \texttt{eval} to instantiate Jobfile objects and the implementation language's (ruby)
 ability to monkeypatch classes means that jobs can be modified on the fly just by sending
@@
 
-Workers are initialized with the~3 computation routines shown in Table~\ref{table:workerTasks}.
+Workers are initialized with the three computation routines shown in Table~\ref{table:workerTasks}.
 
@@
 \subsection{Precision and Recall}
-In order for task killing to be an effective strategy for a top-k computation, the
+For task killing to be an effective strategy for a top-k computation, the
 distribution of words in the corpus must be able to sustain data loss. This is the case
@@
 on good precision in the top~100. Because I use a weighted $F$-score, the poor recall's impact
-on measured accuracy is mitigated.
+on measured accuracy is lessened.
 
@@
 $0.231$ with a standard deviation of $0.025$. I performed four additional experiments with the
-work level set to $0.8$ and $0.4$ with the task kill rate set to $0.1$ and $0.7$. These experiments were
+work level set to $\{0.8,0.4\}$ and with the task kill rate set to $\{0.1,0.7\}$. These experiments were
 not included in generating Figure~\ref{fig:fscore}. The average reduction in $F_{0.5}$-score between
@@
 
-In order to mitigate the effects of this problem, I batched individual requests into groups of~5. This
+To mitigate the effects of this problem, I batched individual requests into groups of~5. This
 lowered the number of connections I was initiating but it also limited the parallelism of the cluster
@@
 
-In order to address this problem, the master needs to keep a persistent channel open between
+To address this problem, the master needs to keep a persistent channel open between
 it and all active nodes. Communication channels should be established when nodes come online.

### 2012-05-11 paper/paper.tex
Run through spellchecker

@@
 How does one decide which data to process then? Ultimately, this is problem dependent;
-however, selctively deciding which data to
+however, selectively deciding which data to
 log is problematic because it can systemically mask some of the trends one would
-try to uncover through analysis. In this paper, I introduce StreamReduce, a distributed system
+try to uncover through analysis. In this paper, I introduce StreamReduce, a distributed
+system
 for processing data streams. With StreamReduce I explore:
@@
 Combining both of these techniques allows the cluster to save time by executing faster,
-save resources by avoiding the need to process every datum, and minimize the impact of faults
+save resources by avoiding the need to process every datum, and minimize the impact of
+faults
 in the execution of a job by treating failed tasks as discarded tasks.
@@
 
-The goal of StreamReduce is to provide a MapReduce-style framework for processing streams. Such a
+The goal of StreamReduce is to provide a MapReduce-style framework for processing
+streams. Such a
 framework should include the ability to kill or discard tasks, be capable of
-providing workers with serveral different computation routines to choose among, and pass data
+providing workers with several different computation routines to choose among, and pass
+data
 between nodes using non-blocking routines.
@@
 
-StreamReduce builds of previous work in the areas of MapReduce, Data Stream Management Systems,
+StreamReduce builds of previous work in the areas of MapReduce, Data Stream Management
+Systems,
 and approximation algorithms.
@@
 \subsection{MapReduce}
-There is a rich research field around MapReduce. This section details work related to adapting
+There is a rich research field around MapReduce. This section details work related to
+adapting
 MapReduce to a streaming environment.
 
-The Hadoop Online Prototype~\cite{Condie:EECS-2009-136} adds streaming to the MapReduce framework
+The Hadoop Online Prototype~\cite{Condie:EECS-2009-136} adds streaming to the
+MapReduce framework
 by removing the materialize phase between mappers and reducers and between phases of a
-MapReduce pipeline. Results are streamed from mappers to reducers as they become available.
+MapReduce pipeline. Results are streamed from mappers to reducers as they become
+available.
 At any given point, each reducer maintains an in-progress snapshot of the MapReduce job's
-progress up to that point. This removes the synchronization barriers inherient in MapReduce
+progress up to that point. This removes the synchronization barriers inherent in MapReduce
 and allows incremental progress to be observed.
 
-This approach is in contrast to the continuous query approach taken by many other streaming
+This approach is in contrast to the continuous query approach taken by many other
+streaming
 systems. StreamReduce uses this snapshot approach.
@@
 append-only stream of tuples. Such
-streams lend themselves to incremental reads and incremental processing. In addition to incremental
-updates, the Chronicle Data Model also seeks to update results incrementally without storing the
+streams lend themselves to incremental reads and incremental processing. In addition to
+incremental
+updates, the Chronicle Data Model also seeks to update results incrementally without storing
+the
 data itself.
 
-The \emph{Data Stream Model}~\cite{Babcock:2002:MID:543613.543615} is a refinement of the Chronicle
+The \emph{Data Stream Model}~\cite{Babcock:2002:MID:543613.543615} is a refinement of
+the Chronicle
 Data Model. It has the following properties: stream items may arrive out of order,
-streams are potentially unbounded in size, and elements in the stream are discared after they are
+streams are potentially unbounded in size, and elements in the stream are discarded after
+they are
 processed. This is the data model that StreamReduce uses.
@@
 In this case, a streaming system would like to implement
-\emph{early phase termination}~\cite{Rinard:2007:UEP:1297027.1297055}, or preemptively kill
+\emph{early phase termination}~\cite{Rinard:2007:UEP:1297027.1297055}, or preemptively
+kill
 a stage in the pipeline that is not capable of keeping all workers busy.
@@
 \texttt{filter}, \texttt{map}, and \texttt{union} for
-manipulating streams. StreamReduce implements these operators at the worker and fetcher nodes.
+manipulating streams. StreamReduce implements these operators at the worker and fetcher
+nodes.
 
 \subsection{Approximation Algorithms}
-An alternative to load shedding to cope with high stream throughput is to perform approximate
+An alternative to load shedding to cope with high stream throughput is to perform
+approximate
 computations on stream data.
 
-Dynamic Knobs~\cite{Hoffmann:2011:DKR:1950365.1950390} describes a mechanism to explore the
-accuracy-performance tradeoff space, dynamically adjusting program tuning parameters in response
+Dynamic Knobs~\cite{Hoffmann:2011:DKR:1950365.1950390} describes a mechanism to
+explore the
+accuracy-performance tradeoff space, dynamically adjusting program tuning parameters in
+response
 to changes in the execution environment. This allows programs to do things such as
@@
 \emph{peak load provisioning}. Their system can adjust downward the amount of resources,
-machines, etc. required for normal load and quickly adjust these levels back up to
+machines, etc\. required for normal load and quickly adjust these levels back up to
 handle load spikes. Combined with Aurora's load shedding, peak load provisioning can
@@
 
-Accuracy-aware transformations~\cite{Zhu:2012:RAP:2103656.2103710} are a class of transformations
-that alter a computation according to a set of probabilstic weights and an accuracy
+Accuracy-aware transformations~\cite{Zhu:2012:RAP:2103656.2103710} are a class of
+transformations
+that alter a computation according to a set of probabilistic weights and an accuracy
 target such that the computation performs more efficiently. StreamReduce uses the subclass
@@
 an opportunity for the results of a computation performed by StreamReduce to be distorted.
-Rinard~\cite{Rinard:2006:PAB:1183401.1183447} describes a method for bounding the distortion
-introduced when discarding tasks. By breaking a computation into tasks, which in StreamReduce
+Rinard~\cite{Rinard:2006:PAB:1183401.1183447} describes a method for bounding the
+distortion
+introduced when discarding tasks. By breaking a computation into tasks, which in
+StreamReduce
 consist of processing an individual datum at a worker, we can measure a
-\emph{probabilistic distortion model} for a job, which gives bounds on its accuracy at different
-task failure rates. I use this approach in the case study discussed in Section~\ref{sec:evaluation}.
+\emph{probabilistic distortion model} for a job, which gives bounds on its accuracy at
+different
+task failure rates. I use this approach in the case study discussed in
+Section~\ref{sec:evaluation}.
 
@@
   \item
-    \textbf{Worker}: Processes data returned by fetchers. They are the source of parallel computation
+    \textbf{Worker}: Processes data returned by fetchers. They are the source of parallel
+computation
     in the cluster.
   \item
-    \textbf{Collector}: Aggregates results from all workers and makes the result accessible via an API.
+    \textbf{Collector}: Aggregates results from all workers and makes the result accessible via
+an API.
   \item
-    \textbf{Master}: Manages the cluster by bringing nodes online to complete jobs. It is reponsible
+    \textbf{Master}: Manages the cluster by bringing nodes online to complete jobs. It is
+responsible
     for all internode communication and storing to-be-processed data in several queues.
@@
 \includegraphics[width=\textwidth]{system-diagram.png}
-\caption{Overview of data flow in the execution of a StreamReduce job. Load shedding occurs at point A. Task killing occurs at point B.}
+\caption{Overview of data flow in the execution of a StreamReduce job. Load shedding
+occurs at point A. Task killing occurs at point B.}
 \label{fig:systemdiagram}
@@
 \subsection{Spout}
-Spouts are network-connected machines that generate data for a StreamReduce cluster to process.
+Spouts are network-connected machines that generate data for a StreamReduce cluster to
+process.
 Examples include a machine that tails a log file or an API like the Twitter tweet
@@
 
-Workers are responsible for fulfilling the main design goals of StreamReduce. Workers may choose
+Workers are responsible for fulfilling the main design goals of StreamReduce. Workers may
+choose
 to kill a task preemptively or, if it does not complete before a timeout, greedily. Additionally,
@@
 
-Because one of StreamReduce's goals is to process (potentially infinite) streams, workers do not
+Because one of StreamReduce's goals is to process (potentially infinite) streams, workers do
+not
 save their progress to disk and are forgetful; once the master queries a worker for its
@@
 can choose to retain copies of individual worker results and re-reduce them each time more
-results are receieved, but this is not in the spirit of the framework.)
+results are received, but this is not in the spirit of the framework.)
 
@@
 \label{sec:master}
-There is one master node per StreamReduce cluster. It has a function similar to the jobtracker in
+There is one master node per StreamReduce cluster. It has a function similar to the
+jobtracker in
 MapReduce. New jobs are scheduled with the master and it initializes other nodes in the
-cluster with job state. For each job, the master schedules roles among nodes in a round robin
+cluster with job state. For each job, the master schedules roles among nodes in a round
+robin
 manner to minimize the total number of outstanding roles on any one node.
 
-The master is the only well-known node in the cluster. Other nodes in the network exclusively
-communicate with the master. The master and other nodes communicate with each other by issuing
-HTTP requests to a simple server on each node. I decided to make use of a library~\cite{sinatrarb}
+The master is the only well-known node in the cluster. Other nodes in the network
+exclusively
+communicate with the master. The master and other nodes communicate with each other by
+issuing
+HTTP requests to a simple server on each node. I decided to make use of a
+library~\cite{sinatrarb}
 providing the server functionality because there was a low barrier to getting inter-node
-communication functioning. This design choice presents some problems and will be discussed
+communication functioning. This design choice presents some problems and will be
+discussed
 further in Section~\ref{sec:discussion}.
@@
 \includegraphics[width=\linewidth]{master-control-queue.png}
-\caption{The master communicates directly with all nodes to pass them control messages. Nodes respond directly to the master with their results.}
+\caption{The master communicates directly with all nodes to pass them control messages.
+Nodes respond directly to the master with their results.}
 \label{fig:mastercontrolqueue}
@@
 
-Figure~\ref{fig:mastercontrolqueue} shows how control messages are passed from the master
+Figure~\ref{fig:mastercontrolqueue} shows how control messages are passed from the
+master
 to all other nodes in the cluster. The master communicates directly to each node and nodes
-reply directly to the master when they have completed their task. With these control messages,
-the master advances the state of the job. Such messages include telling a fetcher to fetch data
+reply directly to the master when they have completed their task. With these control
+messages,
+the master advances the state of the job. Such messages include telling a fetcher to fetch
+data
 from a spout, giving data to a worker to process, and flushing results to collectors.
@@
 Apart from spouts, all nodes in a cluster modify their behavior based on the job they are
-running. The master must know the appropriate number of nodes to spin up; fetchers need to
-know how to talk to spouts; workers need to know how to compute results; and collectors need
+running. The master must know the appropriate number of nodes to spin up; fetchers need
+to
+know how to talk to spouts; workers need to know how to compute results; and collectors
+need
 to know how to combine batched worker results.
 
-StreamReduce achieves this configuration with a Jobfile. Jobfiles are instances of a special class
-provided by the StreamReduce framework. This class exposes several methods that can be invoked by a
+StreamReduce achieves this configuration with a Jobfile. Jobfiles are instances of a special
+class
+provided by the StreamReduce framework. This class exposes several methods that can be
+invoked by a
 given node to provide configuration parameters or execute code on its behalf. Most of the
-routines that advance the progress of a StreamReduce job are wrappers around these Jobfile methods.
+routines that advance the progress of a StreamReduce job are wrappers around these Jobfile
+methods.
 
@@
 \texttt{eval} to
-obtain a local instance of the Jobfile class. An example jobfile can be found at~\cite{github}.
+obtain a local instance of the Jobfile class. An example Jobfile can be found at~\cite{github}.
 
-The use of \texttt{eval} to instantiate Jobfile objects and the implementation language's (ruby)
-ability to monkeypatch classes means that jobs can be modified on the fly just by sending
+The use of \texttt{eval} to instantiate Jobfile objects and the implementation language's
+(ruby)
+ability to monkey-patch classes means that jobs can be modified on the fly just by sending
 an updated Jobfile to job participants. For example, a job can be made lower fidelity in
-the face of an impending time constraint, be made higher fidelity if more workers are added to
+the face of an impending time constraint, be made higher fidelity if more workers are added
+to
 the cluster, or gracefully kill all fetchers which allows the job to end after all of the
@@
 \subsection{Fault Tolerance}
-StreamReduce can sustain the failure of any node other than the master. Because the master is responsible
-for shuffling data between fetchers, workers, and collectors, a job cannot make progress without
+StreamReduce can sustain the failure of any node other than the master. Because the master
+is responsible
+for shuffling data between fetchers, workers, and collectors, a job cannot make progress
+without
 the master.
@@
 Fetchers can fail. The only consequence of fetcher failure is that some of the input stream is
-lost forever. Because StreamReduce uses the Data Stream Model, it does not attempt to recover this data.
+lost forever. Because StreamReduce uses the Data Stream Model, it does not attempt to
+recover this data.
 
-Worker failures may entail some lost work. Having the master poll each worker frequently for its
-progress mitigates the consequences of worker failure. For jobs that run for minutes or hours,
-100ms of lost work is $\ll0.1\%$ of the total. StreamReduce can simply treat these lost tasks as preemptively
+Worker failures may entail some lost work. Having the master poll each worker frequently for
+its
+progress mitigates the consequences of worker failure. For jobs that run for minutes or
+hours,
+100ms of lost work is $\ll0.1\%$ of the total. StreamReduce can simply treat these lost tasks
+as preemptively
 killed, which is already expected by the cluster.
 
-Each collector is an exact replica of all others. Collector failure does not impact correctness of
-the results delivered by any other collector. If no collectors are online, the data meant for them
-sits in a queue on the master. Bringing another collector online will allow these and future results
+Each collector is an exact replica of all others. Collector failure does not impact correctness
+of
+the results delivered by any other collector. If no collectors are online, the data meant for
+them
+sits in a queue on the master. Bringing another collector online will allow these and future
+results
 to be aggregated.
 \subsection{Killing Tasks and Working Less}
-A design goal of StreamReduce is to compute meaningful results from a stream and to do so while not
-processing every datum one-to-one. StreamReduce achieves this goal in two different ways. First, workers
+A design goal of StreamReduce is to compute meaningful results from a stream and to do so
+while not
+processing every datum one-to-one. StreamReduce achieves this goal in two different ways.
+First, workers
 may kill tasks preemptively to avoid the time and resource costs associated with processing
@@
 \label{sec:methodology}
-The cluster I used to test StreamReduce is a 5-node network consisting of~1 spout,~1 fetcher,~4 workers,~1
+The cluster I used to test StreamReduce is a 5-node network consisting of~1 spout,~1
+fetcher,~4 workers,~1
 collector, and~1 master. Roles were partitioned among nodes as shown in
-Figure~\ref{fig:clusterDiagram}. Worker nodes were XVM~\cite{sipb:xvm} VMs provisioned with~128MB RAM each.
-The master, spout, fetcher, and collector ran on a mid-2010 Macbook Air laptop with~4GB of RAM. I configured
+Figure~\ref{fig:clusterDiagram}. Worker nodes were XVM~\cite{sipb:xvm} VMs provisioned
+with~128MB RAM each.
+The master, spout, fetcher, and collector ran on a mid-2010 Macbook Air laptop with~4GB of
+RAM\@. I configured
 the cluster to kill tasks on the master node, before they were shipped to workers.
@@
 \includegraphics[width=\linewidth]{sr-topology.png}
-\caption{Topology of the test StreamReduce cluster used in the word count case study. Each square box represents a single machine. Each rounded box represents a StreamReduce role.}
+\caption{Topology of the test StreamReduce cluster used in the word count case study. Each
+square box represents a single machine. Each rounded box represents a StreamReduce role.}
 \label{fig:clusterDiagram}
@@
 
-The job I ran was a word counter. The collector emits a hash whose keys are words and whose
+The job I ran was a word counter. The collector emits a hash whose keys are words and
+whose
 values are the frequency the key occurred in the test corpus.
@@
 
-The fetcher communicates to the spout by requesting sequential article ids until it has fetched
+The fetcher communicates to the spout by requesting sequential article ids until it has
+fetched
 every article.
 
-Workers are initialized with the three computation routines shown in Table~\ref{table:workerTasks}.
+Workers are initialized with the three computation routines shown in
+Table~\ref{table:workerTasks}.
 
@@
 1.0 & Deflate and decode fulltext and count words in all of fulltext \\ \hline
-0.25 & Deflate and decode fulltext and count words in approximately a quarter of fulltext \\ \hline
+0.25 & Deflate and decode fulltext and count words in approximately a quarter of fulltext \\
+\hline
 0.1 & Return the results of the last computation from a cache \\ \hline
@@
 The cluster and word count job could be used in a two-stage top-k job. This script filters
-out SEO stopwords~\cite{stopwords} to achieve more interesting results.
+out SEO stop words~\cite{stopwords} to achieve more interesting results.
 
@@
 \label{sec:evaluation}
-To evaluate StreamReduce, I explore the precision and recall of the word count test job as well as the
+To evaluate StreamReduce, I explore the precision and recall of the word count test job as
+well as the
 speedup factor associated with varying the task kill rate and target work level.
@@
 \includegraphics[width=\linewidth]{long-tail-ranks.png}
-\caption{The frequencies of words in the Wikipedia Featured Articles corpus have a long-tailed distribution. This graph has had stopwords~\cite{stopwords} filtered out of it.}
+\caption{The frequencies of words in the Wikipedia Featured Articles corpus have a long-
+tailed distribution. This graph has had stop words~\cite{stopwords} filtered out of it.}
 \label{fig:wordDist}
@@
 \subsubsection{Recall}
-Recall in the tail of the distribution is most dependent on the work level of the word count job.
+Recall in the tail of the distribution is most dependent on the work level of the word count
+job.
 Anything less than perfect computation of a datum leaves out words with a frequency of one.
@@
 the same effect on recall as using low fidelity computation routines, so recall decreases as
-the task kill rate does. Task killing dominates the impact of work level on recall as demonstrated
+the task kill rate does. Task killing dominates the impact of work level on recall as
+demonstrated
 by the two lines converging in Figure~\ref{fig:recall}.
@@
 Poor recall statistics are acceptable because I am running a top-k job that focuses
-on good precision in the top~100. Because I use a weighted $F$-score, the poor recall's impact
+on good precision in the top~100. Because I use a weighted $F$-score, the poor recall's
+impact
 on measured accuracy is lessened.
@@
 \includegraphics[width=\linewidth]{recall.png}
-\caption{Fraction of the bottom~10000 results returned in the result set by the word count job.}
+\caption{Fraction of the bottom~10000 results returned in the result set by the word count
+job.}
 \label{fig:recall}
@@
 \subsubsection{Word Count Job Accuracy}
-Because I am running a top-k job, I compute the $F_{0.5}$-score of the StreamReduce results as
+Because I am running a top-k job, I compute the $F_{0.5}$-score of the StreamReduce
+results as
 opposed to the $F1$-score because I care more about precision of the top k than recall
@@
 \includegraphics[width=\linewidth]{f-score.png}
-\caption{$F_{0.5}$-score for the top-100 word count job.
-I measured the $F$-score with $\beta=0.5$ because the goal of the job is to run a top-k filter on it, meaning I care more about precision than recall.}
+\caption{$F_{0.5}$-score for the top-100 word count job. I measured the $F$-score with
+$\beta=0.5$ because the goal of the job is to run a top-k filter on it, meaning I care more
+about precision than recall.}
 \label{fig:fscore}
@@
 
-The average reduction in $F_{0.5}$-score caused by reducing the work level form 0.8 to 0.4 is
-$0.231$ with a standard deviation of $0.025$. I performed four additional experiments with the
-work level set to $\{0.8,0.4\}$ and with the task kill rate set to $\{0.1,0.7\}$. These experiments were
-not included in generating Figure~\ref{fig:fscore}. The average reduction in $F_{0.5}$-score between
+The average reduction in $F_{0.5}$-score caused by reducing the work level form 0.8 to 0.4
+is
+$0.231$ with a standard deviation of $0.025$. I performed four additional experiments with
+the
+work level set to $\{0.8,0.4\}$ and with the task kill rate set to $\{0.1,0.7\}$. These
+experiments were
+not included in generating Figure~\ref{fig:fscore}. The average reduction in $F_{0.5}$-score
+between
 work level $0.8$ and $0.4$ in these experiments is $0.230$ with a standard deviation of
-$0.056$. These numbers show that a $0.4$ reduction in the work level leads to approximately a
+$0.056$. These numbers show that a $0.4$ reduction in the work level leads to
+approximately a
 $0.23$ reduction in $F_{0.5}$-score.
@@
 \subsection{Speedup}
-StreamReduce is able to achieve a speedup over a MapReduce-style computation through three mechanisms:
+StreamReduce is able to achieve a speedup over a MapReduce-style computation through
+three mechanisms:
 providing multiple computation routines for the workers to choose from; varying the task kill
-rate; and varying the target work level, which influences the chosen frequency of computation
+rate; and varying the target work level, which influences the chosen frequency of
+computation
 routines per worker.
 
-Table~\ref{table:runtime} shows the effect of varying the task kill rate and work level. The row
-with kill~rate~$=0.0$ and work~level~$=1.0$ represents the perfect, MapReduce-style, execution
+Table~\ref{table:runtime} shows the effect of varying the task kill rate and work level. The
+row
+with kill~rate~$=0.0$ and work~level~$=1.0$ represents the perfect, MapReduce-style,
+execution
 of the word count job. The only consistent reduction in execution time is a result of
-increasing the task kill rate. Increasing the task kill rate exhibits a linear reduction in execution
+increasing the task kill rate. Increasing the task kill rate exhibits a linear reduction in
+execution
 time as the fraction of processed data linearly decreases.
@@
 
-Notably, simply by killing tasks, StreamReduce is able to achieve over a~5 times speedup compared
+Notably, simply by killing tasks, StreamReduce is able to achieve over a~5 times speedup
+compared
 to the perfect execution while still returning about~84 of the top~100 words.
@@
   \end{tabularx}
-  \caption{Example top~10 results and their frequencies from several different job configurations. The top~10 do not change much one changes the paramters to make the job less accurate.}
+  \caption{Example top~10 results and their frequencies from several different job
+configurations. The top~10 do not change much one changes the parameters to make the job
+less accurate.}
   \label{table:top10}
@@
 Additionally, Table~\ref{table:runtime} shows that the most significant time savings comes
-from increasing the kill rate and keeping the work level high yields about a~20 percentage point
+from increasing the kill rate and keeping the work level high yields about a~20 percentage
+point
 increase in $F_{0.5}$-score.
@@
 \label{sec:discussion}
-This section describes deficiencies in the implementation of StreamReduce used to run the case study
+This section describes deficiencies in the implementation of StreamReduce used to run the
+case study
 in this paper and goals for the next version of the system.
@@
 \subsection{On-the-Fly Job Reconfiguration}
-The mechanism for altering execution of a job as it is running described in Section~\ref{sec:jobfile}
-is not yet implemented. Adding this feature to StreamReduce is a matter of adding an API endpoint
+The mechanism for altering execution of a job as it is running described in
+Section~\ref{sec:jobfile}
+is not yet implemented. Adding this feature to StreamReduce is a matter of adding an API
+endpoint
 to the servers run by each role and adding a bin-script to submit the new Jobfile.
@@
 \subsection{Internode Communication}
-In Section~\ref{sec:master} I mentioned design difficulties relating to the master and using HTTP
-requests for sending messages between nodes. I initially chose to use HTTP requests with POST payloads
-to send data and results between nodes because of its low barrier to entry; however, initiating many
-HTTP requests in succession is expensive. When killing jobs on worker nodes, the observed time savings
-was minimal because most of the time spent per datum involved shipping it from the master to the worker.
+In Section~\ref{sec:master} I mentioned design difficulties relating to the master and using
+HTTP
+requests for sending messages between nodes. I initially chose to use HTTP requests with
+POST payloads
+to send data and results between nodes because of its low barrier to entry; however,
+initiating many
+HTTP requests in succession is expensive. When killing jobs on worker nodes, the observed
+time savings
+was minimal because most of the time spent per datum involved shipping it from the master
+to the worker.
 
 To mitigate the effects of this problem, I batched individual requests into groups of~5. This
-lowered the number of connections I was initiating but it also limited the parallelism of the cluster
-and removed workers from the pool for longer periods because they had more data to process at a time.
+lowered the number of connections I was initiating but it also limited the parallelism of the
+cluster
+and removed workers from the pool for longer periods because they had more data to
+process at a time.
 A killed task on the worker no longer freed it up to receive a new task immediately.
-Keeping workers removed from the pool caused the queues on the master to grow longer as the workers
+Keeping workers removed from the pool caused the queues on the master to grow longer as
+the workers
 could no longer keep up with the rate the fetcher was producing data.
@@
 decides to discard a task as it is popped from the queue, before it is ever sent to a worker.
-Doing so improved the execution time of the cluster but also meant that workers no longer had
+Doing so improved the execution time of the cluster but also meant that workers no longer
+had
 a full idea of how accurate they were being because they never killed any tasks themselves.
@@
 To address this problem, the master needs to keep a persistent channel open between
-it and all active nodes. Communication channels should be established when nodes come online.
+it and all active nodes. Communication channels should be established when nodes come
+online.
 Possible solutions include writing to a socket or using a higher abstraction like AMPQ\@.
@@
 \subsection{Node Health}
-Currently, the master does not probe nodes to ensure that they are responsive. In the case that
+Currently, the master does not probe nodes to ensure that they are responsive. In the case
+that
 a node is serving a worker role for a job, this deficiency is masked. The node will simply not
-return the HTTP request sent to it to push it some data and the worker will remain removed from
+return the HTTP request sent to it to push it some data and the worker will remain removed
+from
 the pool. If the node is in the role of fetcher or collector, the master will stall.
@@
 \subsection{Job Management}
-There is no support for killing jobs or removing them from the master's data structures. The only
+There is no support for killing jobs or removing them from the master's data structures. The
+only
 way to remove a job is to kill the master and all other nodes in the cluster.
@@
 \section{Conclusion}
-I have extended the ideas of approximate computations to a MapReduce-style framework and shown
+I have extended the ideas of approximate computations to a MapReduce-style framework
+and shown
 that it is feasible to tune the input parameters of a job to achieve sufficient precision and
@@
 
-I have taken a different approach to streaming MapReduce by treating data not as a batch, but
+I have taken a different approach to streaming MapReduce by treating data not as a batch,
+but
 as a stream. At any given point in the execution of a job, the collectors will have accurate
 (so far as the job parameters allow) results for data seen until that point. This approach
-guarantees freshness and makes it easier to incorporate new data into an existing computation,
+guarantees freshness and makes it easier to incorporate new data into an existing
+computation,
 yet it suffers from being limited to online aggregations.

### 2012-05-11 paper/paper.tex
Pretty multiline column header

@@
     \hline
-    \multicolumn{2}{|X|}{Work level = 1.0 and task kill rate = 0.0} &
-    \multicolumn{2}{|X|}{Work level = 0.8 and task kill rate = 0.4} &
-    \multicolumn{2}{|X|}{Work level = 0.4 and task kill rate = 0.8} \\ \hline
+    \multicolumn{2}{|X|}{\begin{tabular}[x]{l}Work level = 1.0 \\ Task kill rate = 0.0\end{tabular}} &
+    \multicolumn{2}{|X|}{\begin{tabular}[x]{l}Work level = 0.8 \\ Task kill rate = 0.4\end{tabular}} &
+    \multicolumn{2}{|X|}{\begin{tabular}[x]{l}Work level = 0.4 \\ Task kill rate = 0.8\end{tabular}} \\ \hline
     33225 & title & 21184 & title & 5982 & title \\ \hline

### 2012-05-11 paper/paper.tex
Add UAP completion comment to acknowledgments
Better title
Another editing round

@@
 
-\title{StreamReduce: Processing Data Streams\\and Avoiding Work}
+\title{StreamReduce: A Data Stream Processor with MapReduce Parallelism}
 \author{Ryan Lopopolo\\
@@
 the job with the new data included. Others have solved this problem by batching data
-into chunks and continuously spawning MapReduce jobs to incorporate the new data
+into chunks, continuously spawning MapReduce jobs to incorporate the new data,
 and incrementally storing updates in an external database instead of relying on
@@
 explore the
-accuracy-performance tradeoff space, dynamically adjusting program tuning parameters in
+accuracy--performance tradeoff space, dynamically adjusting program tuning parameters in
 response
@@
 different types of nodes in a StreamReduce cluster:
-\begin{itemize}
-  \item
-    \textbf{Spout}: A node external to the cluster that is a source of streaming data.
-  \item
-    \textbf{Fetcher}: Communicates with spouts to provide data for workers.
-  \item
-    \textbf{Worker}: Processes data returned by fetchers. They are the source of parallel
+\begin{description}
+  \item[Spout] A node external to the cluster that is a source of streaming data.
+  \item[Fetcher] Communicates with spouts to provide data for workers.
+  \item[Worker] Processes data returned by fetchers. They are the source of parallel
 computation
     in the cluster.
-  \item
-    \textbf{Collector}: Aggregates results from all workers and makes the result accessible via
+  \item[Collector] Aggregates results from all workers and makes the result accessible via
 an API.
-  \item
-    \textbf{Master}: Manages the cluster by bringing nodes online to complete jobs. It is
+  \item[Master] Manages the cluster by bringing nodes online to complete jobs. It is
 responsible
     for all internode communication and storing to-be-processed data in several queues.
-\end{itemize}
-Figure~\ref{fig:systemdiagram} shows a system diagram of StreamReduce.
+\end{description}
+Figure~\ref{fig:systemdiagram} shows a system diagram of a StreamReduce cluster.
 
@@
 Examples include a machine that tails a log file or an API like the Twitter tweet
-stream. Fetchers depend on spouts as a source of streaming data.
+stream~\cite{twitter}. Fetchers depend on spouts as a source of streaming data.
 \subsection{Fetcher}
@@
 configurations: A spout can emit data at such a high rate that using multiple fetchers
-returns more data to the cluster, multiple fetchers can each talk to a different spout,
-for example tailing logs from multiple machines, or fetchers can be set up redundantly
+returns more data to the cluster; multiple fetchers can each talk to a different spout,
+for example tailing logs from multiple machines; or fetchers can be set up redundantly
 to ensure that every datum emitted by a spout is processed.
@@
 workers may choose among a variety of routines for performing computation on a datum.
-Routines are ranked on a [0,1] scale based on the estimated fraction of total work it
+Routines are ranked on a $[0,1]$ scale based on the estimated fraction of total work it
 requires. This rank is a proxy for the accuracy of a routine.
@@
 The total work estimator is used as a proxy for accuracy when a worker updates
-this metric. This metric also takes into account the number of tasks it has killed
+this metric. This metric also takes into account the number of tasks a worker has killed
 for any reason.
 
-Because one of StreamReduce's goals is to process (potentially infinite) streams, workers do
+Because one of StreamReduce's goals is to process potentially infinite streams, workers do
 not
@@
 library~\cite{sinatrarb}
-providing the server functionality because there was a low barrier to getting inter-node
+providing the server functionality because there was a low barrier to getting internode
 communication functioning. This design choice presents some problems and will be
@@
 cluster must flow through it. The master maintains two queues per job for buffering job
-progress from fetchers and workers and periodically pushes this state out to workers and
-collectors, respectively.
+progress from fetchers, the data queue, and workers, the result queue, and periodically
+pushes this state out to workers and collectors, respectively.
 
@@
 
-\begin{figure}
+\begin{figure}[t]
 \includegraphics[width=\linewidth]{sr-topology.png}
@@
 To run the job, I had to create a spout and find a source of data. For data, I acquired a
-Wikipedia dump of the Featured Articles category. I used Wikipedia's xml
+Wikipedia dump of the Featured Articles category. I used Wikipedia's XML
 exporter~\cite{wikipedia:special:export} on January~9,~2012.
@@
 \end{center}
+
 To store fulltext, I base64 encoded it and
@@
 routines per worker.
+
+Running the perfect computation on one node took 1088 seconds. Compared to the fastest time
+in Table~\ref{table:runtime} using 4 workers, this is over a~700\% speedup. There is much to
+be gained by processing data in parallel.
 
@@
 
+This paper was written in fulfillment of the MIT Course VI Undergraduate Advanced Project
+requirement.
+
 \bibliography{paper}{}

### 2012-05-11 paper/paper.tex
Last edits

@@
 \subsection{Precision and Recall}
-For task killing to be an effective strategy for a top-k computation, the
+For task killing to be an effective strategy in a top-k computation, the
 distribution of words in the corpus must be able to sustain data loss. This is the case
@@
 speed up the calculation by killing tasks without having to sacrifice too much accuracy.
+Table~\ref{table:top10} demonstrates how little the top~10 changes in response to varying
+the job parameters.
 Additionally, Table~\ref{table:runtime} shows that the most significant time savings comes

### 2012-05-15 paper/paper.tex
Incorporate edits from Martin
I had a couple of typos and redid section 5.1, 5.1.1, and 5.1.2.
Talked about the stability of the word count distribution and how
stability influences the effectiveness of a task killing framework

@@
 \emph{peak load provisioning}. Their system can adjust downward the amount of resources,
-machines, etc\. required for normal load and quickly adjust these levels back up to
+machines, etc\@. required for normal load and quickly adjust these levels back up to
 handle load spikes. Combined with Aurora's load shedding, peak load provisioning can
@@
 \subsection{Precision and Recall}
-For task killing to be an effective strategy in a top-k computation, the
-distribution of words in the corpus must be able to sustain data loss. This is the case
-if the distribution is long-tailed, but is not true if the distribution is uniform.
+For task killing to be an effective strategy in a top-k computation,
+the distribution of the top-k words must be stable. A stable distribution is one
+that is not altered by adding an additional article to or removing the last
+article from the corpus. Stable distributions are able to sustain the data lost in
+an approach like task killing.
+
+Every data set has some base level of noise in it due to such things as how the data is
+sampled. StreamReduce introduces another source of noise by discarding data and
+substituting computation algorithms. If the noise introduced by StreamReduce is less than
+the data set's sensitivity to noise, the top-k words remain stable.
+
+For example, if the distribution of words in the test corpus is close to uniform, the top-k
+words are bunched together and any perturbations in the tested data, for example, discarding an
+article that contains instances of the real top-k words, will affect the fidelity of the
+reported top-k.
 
@@
 \includegraphics[width=\linewidth]{long-tail-ranks.png}
-\caption{The frequencies of words in the Wikipedia Featured Articles corpus have a long-
-tailed distribution. This graph has had stop words~\cite{stopwords} filtered out of it.}
+\caption{The frequencies of words in the Wikipedia Featured Articles corpus have a
+long-tailed distribution. This graph has had stop words~\cite{stopwords} filtered out of it.}
 \label{fig:wordDist}
@@
 
-The distribution shown in Figure~\ref{fig:wordDist} is long-tailed. This implies that killing
-tasks will impact the tail of the distribution more than the head.
+The distribution of words in the Wikipeida data set is
+shown in Figure~\ref{fig:wordDist}. The distribution is long-tailed, which is a first step
+in verifying that this data set has a stable top k.
 
 \subsubsection{Precision}
-Task killing should least impact the head of the word distribution.
+For the results given by StreamReduce's top-k computation to be meaningful,
+it is important for the distribution of the top-k words to be stable, which implies
+that task killing minimally impacts the head of the word distribution.
+Table~\ref{table:top10} shows the top-10 words and their frequencies. Within the true top-10
+words, the first word occurs twice as often as the tenth word, and the difference in frequencies
+of adjacently ranked words varies from~400--4000. Given that the data set has approximately~16 million
+words and~3500 articles, there are about~4500 words in any given article. Even the most frequently
+occuring words only appears on average~8 times per article. Gaps in the hundreds are stable in the
+addition or removal of tens of articles.
+
 Figure~\ref{fig:precision} shows that even with a task kill rate of~0.8 and a work level of~0.4,
@@
 \subsubsection{Recall}
-Recall in the tail of the distribution is most dependent on the work level of the word count
-job.
+Recall is sensitive to the stability of the distribution in the tail. Given that the Wikipedia
+data set is long-tailed, the tail of the distribution is very unstable. All of the words
+in the bottom-10000 have frequencies in the single digits. Because the distribution in the
+tail is so tightly-bunched, recall in the tail of the distribution is most dependent on the
+work level of the word count job. Less task killing and higher-fidelity worker computations
+benefit recall.
+
 Anything less than perfect computation of a datum leaves out words with a frequency of one.
@@
 the task kill rate does. Task killing dominates the impact of work level on recall as
-demonstrated
-by the two lines converging in Figure~\ref{fig:recall}.
+demonstrated by the two lines converging in Figure~\ref{fig:recall}.
 
@@
 on good precision in the top~100. Because I use a weighted $F$-score, the poor recall's
-impact
-on measured accuracy is lessened.
+impact on measured accuracy is lessened.
 

### 2012-05-15 paper/paper.tex
Talk about stability in terms of r = f(i)
combinations of inputs and transformations

@@
 \subsection{Precision and Recall}
-For task killing to be an effective strategy in a top-k computation,
-the distribution of the top-k words must be stable. A stable distribution is one
-that is not altered by adding an additional article to or removing the last
-article from the corpus. Stable distributions are able to sustain the data lost in
-an approach like task killing.
+StreamReduce transforms some input into a result. The transformation is affected by
+the substitution transformations and descisions to kill tasks that workers make.
+The result of a StreamReduce computation is sensitive to the properties of the input
+and the the properties of the transformation applied.
 
@@
 sampled. StreamReduce introduces another source of noise by discarding data and
-substituting computation algorithms. If the noise introduced by StreamReduce is less than
-the data set's sensitivity to noise, the top-k words remain stable.
+substituting computation algorithms. Certain combinations of inputs and transformations
+may be able to withstand this additional noise while other combinations of inputs and
+transformations may not.
 
 For example, if the distribution of words in the test corpus is close to uniform, the top-k
-words are bunched together and any perturbations in the tested data, for example, discarding an
-article that contains instances of the real top-k words, will affect the fidelity of the
-reported top-k.
+words are bunched together and any perturbations in the transformation,
+such as discarding an
+article that contains instances of the real top-k words, may affect the fidelity of the
+reported top-k. However, if there is sufficient separation among words in the input,
+transformations that discard words may still report an accurate top-k.
+
+%If the noise introduced by StreamReduce is less than
+%the data set's sensitivity to noise, the top-k words remain stable.
+
+%For task killing to be an effective strategy in a top-k computation,
+%the distribution of the top-k words must be stable. A stable distribution is one
+%that is not altered by adding an additional article to or removing the last
+%article from the corpus. Stable distributions are able to sustain the data lost in
+%an approach like task killing.
 
@@
 The distribution of words in the Wikipeida data set is
-shown in Figure~\ref{fig:wordDist}. The distribution is long-tailed, which is a first step
-in verifying that this data set has a stable top k.
+shown in Figure~\ref{fig:wordDist}. The distribution is long-tailed, which may indicate
+that this data set can withstand the perturbations introduced by StreamReduce.
 
@@
 For the results given by StreamReduce's top-k computation to be meaningful,
-it is important for the distribution of the top-k words to be stable, which implies
-that task killing minimally impacts the head of the word distribution.
+it is important for the distribution of the top-k words to be resistant to perturbations,
+which implies that task killing minimally impacts the head of the word distribution.
 Table~\ref{table:top10} shows the top-10 words and their frequencies. Within the true top-10
@@
 words and~3500 articles, there are about~4500 words in any given article. Even the most frequently
-occuring words only appears on average~8 times per article. Gaps in the hundreds are stable in the
-addition or removal of tens of articles.
+occuring word only appears on average~8 times per article.
+%Gaps in the hundreds are stable in the
+%addition or removal of tens of articles.
+
+Table~\ref{table:top10} and Figure~\ref{fig:precision} show that the Wikipedia
+data set has sufficient spacing in the head of its distribution to withstand the
+data-discarding transformations that StreamReduce employs.
 
@@
 \subsubsection{Recall}
-Recall is sensitive to the stability of the distribution in the tail. Given that the Wikipedia
-data set is long-tailed, the tail of the distribution is very unstable. All of the words
+Recall is sensitive to the tail of the distribution. Given that the Wikipedia
+data set is long-tailed, the distribution's tail is very uniform. All of the words
 in the bottom-10000 have frequencies in the single digits. Because the distribution in the
-tail is so tightly-bunched, recall in the tail of the distribution is most dependent on the
+tail is so tightly-bunched, recall in the tail of the distribution may be impacted heavily
+by the distortions introduced by StreamReduce. Recall tends to be most dependent on the
 work level of the word count job. Less task killing and higher-fidelity worker computations
-benefit recall.
+seem to benefit recall.
 

### 2012-05-15 paper/paper.tex
More edits

@@
 the substitution transformations and descisions to kill tasks that workers make.
-The result of a StreamReduce computation is sensitive to the properties of the input
-and the the properties of the transformation applied.
+The result of a StreamReduce computation may be affected by the properties of the input
+and the properties of the transformation applied.
 
@@
 sampled. StreamReduce introduces another source of noise by discarding data and
-substituting computation algorithms. Certain combinations of inputs and transformations
-may be able to withstand this additional noise while other combinations of inputs and
-transformations may not.
+substituting computation algorithms. For certain combinations of inputs and transformations,
+this additional noise may have very little impact on the result
+while for other combinations, the impact may be larger.
 
@@
 occuring word only appears on average~8 times per article.
-%Gaps in the hundreds are stable in the
-%addition or removal of tens of articles.
+
+This significant spacing in the top~100 words makes it likely that the input will produce an
+accurate result when StreamReduce transforms it by discarding data.
 
@@
 data set has sufficient spacing in the head of its distribution to withstand the
-data-discarding transformations that StreamReduce employs.
+data-discarding transformations that StreamReduce employs. The top~100 always includes at
+least~86 of the top~100 words and in most cases includes more than~90 of the top~100.
 
-Figure~\ref{fig:precision} shows that even with a task kill rate of~0.8 and a work level of~0.4,
-meaning that the cluster only looks at 8\% of the words in the corpus, the results
+Figure~\ref{fig:precision} shows that even when the input is processed by a transformation that deviates
+from perfect-fidelity, StremReduce still returns meaningful results.
+When transforming the input with a task kill rate of~0.8 and a work level of~0.4,
+meaning that the cluster only looks at~8\% of the words in the corpus, the results
 are at least~80\% accurate. Increasing the work level, which increases the fidelity of

### 2012-05-16 paper/paper.tex
Final edits

@@
 reported top-k. However, if there is sufficient separation among words in the input,
-transformations that discard words may still report an accurate top-k.
+transformations that discard words should still report an accurate top-k.
 
@@
 The distribution of words in the Wikipeida data set is
-shown in Figure~\ref{fig:wordDist}. The distribution is long-tailed, which may indicate
-that this data set can withstand the perturbations introduced by StreamReduce.
+shown in Figure~\ref{fig:wordDist}. The distribution is long-tailed, which indicates
+that the result from this data set should be robust in the face of
+the perturbations introduced by StreamReduce.
+%this data set can withstand the perturbations introduced by StreamReduce.
 
@@
 
-This significant spacing in the top~100 words makes it likely that the input will produce an
-accurate result when StreamReduce transforms it by discarding data.
+This significant spacing in the top~100 words makes it likely that
+StreamReduce will produce an accurate result when transforming this particular input.
 
@@
 
-Anything less than perfect computation of a datum leaves out words with a frequency of one.
+Anything less than perfect computation of a datum may leave out words with a frequency of one.
 Figure~\ref{fig:recall} shows how recall improves as the work level increases. Task killing has
